### 2018-09-14 docs/lab_meeting_1/main.tex
Start working on slides for NIH site visit presentation

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% LaTeX Template: Beamer arrows
%
% Source: http://www.texample.net/
% Feel free to distribute this template, but please keep the
% referal to TeXample.net.
% Date: Nov 2006
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% How to use writeLaTeX: 
%
% You edit the source code here on the left, and the preview on the
% right shows you the result within a few seconds.
%
% Bookmark this page and share the URL with your co-authors. They can
% edit at the same time!
%
% You can upload figures, bibliographies, custom classes and
% styles using the files menu.
%
% If you're new to LaTeX, the wikibook is a great place to start:
% http://en.wikibooks.org/wiki/LaTeX
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{beamer} %
\usetheme{Boadilla}
\usepackage[latin1]{inputenc}
\usefonttheme{professionalfonts}
\usepackage{times}
\usepackage{tikz}
\usepackage{amsmath}
\usepackage{verbatim}
\usetikzlibrary{arrows,shapes}

\title{Tumor Invasive Scores vs. K14 Expression}
\author{Yohannes Tsehay}
%\title{Spectral Analysis}
\institute{Joel Bader's Lab}
\date{07/17/2018}
\logo{\includegraphics[height=1.5cm]{hopkinslogo.jpg}}

\begin{document}

\tikzstyle{every picture}+=[remember picture]

\everymath{\displaystyle}

\frame{\titlepage}

\begin{frame}
\frametitle{Overview}

\begin{itemize}
		\item Background Information
		\item Objective
		\item Methods
		\item Results
		\item Discussion
		\item Future Directions
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Background}

\begin{itemize}
		\item Metastasis is one of the main determinants of patient prognosis 
		\item Mortality is often due to systemic spread of tumor and not in situ proliferation
		\begin {Example}
		5-year survival rate for invasive breast cancer at diagnosis is:
		\begin {itemize}
	\item 99\% for patient with \alert{local tumors}
	\item 85\% for patients with \alert{regional spread}
	\item 26\% for those with \alert{tumors that have spread to distance organs} \cite{tarver2012cancer}
		\end {itemize}
		\end {Example}
		\item Currently, the molecular mechanism of metastasis is not well understood
		\item Neoplastic drug interventions mostly target proliferation, not metastatic transformation
\end{itemize}

\end{frame}

\begin{frame}
	\frametitle{Quantifying the Invasive Potential of Tumors}
	\begin{itemize}
		\item Why would we need to make a system that quantifies the invasive potential of tumors?
		\begin{itemize}
				\item Quantitative phenotypes are more amenable to systemic analysis
				\item They can be used in population genetics methods, where genetic variations and invasive potential of tumors can be studied by directly perturbing candidate genes
				\item Such studies can lead to the discovery of new drugs for cancer therapy which can ultimately have a positive impact on the poor prognosis seen in patients with metastatic carcinoma 		\end{itemize}
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Related Research Work and Current Developments}
	\begin{itemize}
			\item A quantitative model to study and characterize metastasis has yet to be developed
			\item \cite{shamir2014twist1} challenge the epithelial-to-mesenchymal transition requirement for metastasis, and instead, provide evidence in support of a model based on Twist1 induced dissemination of cytokeratin positive epithelial cells
			\item \cite{cheung2016polyclonal} demonstrated that tumor cells can invade and metastasize in clusters challenging the single-cell/single-metastasis model
			\item They further study how Keratin 14, a known molecular biomarker for metastasis, expressing cells intiate and complete the metastatic process 
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Project Objective}
		The first aim of the project will be to test the hypothesis that K14 is directly correlated with invasiveness versus the alternative hypothesis that organoid size drives both K14 expression and invasion 
\end{frame}

\begin{frame}
	\frametitle{Our Data}
	\begin{itemize}
			\item MMTV-PyMT transgenic mice were be used to produce a supply of organoids
			\item Tumors were removed from 4 mice and a total of 90 - 150 small and large organoids were generated per tumor ($\approx$ 300 organoids in total per tumor)
			\item The organoids were imaged using differential interference contrast (DIC) microscopy
			\item The images were manually traced using \alert{$ImageJ$} to define organoid boundaries
			\item corresponding K14 images are available
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Our Computer Model (Spectral Power)}
	\begin{itemize}
		\item the manually traced boundary is defined by a pair of points \(\{x_v, y_v\}\) for $p \in [0, P-1]$, where $P$ is the total number of points
		\item First the overall length $L$ was calculated
		\item $L = \sum_{v=1}^{V-1} \sqrt{(x_v - x_{v-1})^2 + (y_v - y_{v-1})^2}$
		\item Next, an equally spaced grid was defined with distance $L/M$ between adjacent points, where $M=128$
		\item Then, linear interpolation was used to generate a new boundary with equally spaced points \(\{x_j, y_j\}\), where $j \in \{0,1,...,M-1\}$  
	\end{itemize}
\end{frame}

\begin{frame}
	\begin{itemize}
			\item Then, a fast Fourier transform on the newly generated boundary is performed according to:
			\newline
			$\hat{x}_k = \sum_{j=0}^{M-1} e^{-2\pi ijk/M} x_j$ 
			\newline
			$\hat{y}_k = \sum_{j=0}^{M-1} e^{-2\pi ijk/M} y_j$ 
			\item where $k \in \{0,1,...,M/2+1\}$
	\end{itemize}
\end{frame}

\begin{frame}
	\begin{itemize}
			\item The spectral power $P_k$ is given by:
			\newline
			$P_k = |\hat{x}_k|^2 + |\hat{y}_k|^2$
			\newline
			\item where $k \in \{0,1,...,M/2+1\}$
			\item $P_0$ is the center and $P_1$ is used to normalize the total power given by:
			\newline
			$P_{total} = \sum_{k=2}^{M/2+1} P_k/P_1$
			\item this produces a spectral power that is scale invariant in addition to being transilation and rotation invariant. 
	\end{itemize}
\end{frame}

\begin{frame}
	\begin{itemize}
			\item Means and parametric derivative transforms are estimated
			\item This is done to smooth out artifacts in the boundary 
			\item The transform for $\bar{x}_{j\prime} \equiv (x_{j\prime+1/2} + x_{j\prime-1/2})/2$ is: 
			\newline
			$\hat{\bar{x}}_k = \cos(\pi k/M)\hat{x}$ 
			\newline
			\item The transform for $\dot{x}$ is: 
			\newline
			$\hat{\dot{x}} = (iM/\pi)\sin(\pi k/M)\hat{x}$
			\item Therefore, the final weighted spectral power becomes:
			\newline
			$w \equiv \sum_{k=2}^{M/2} (M/\pi)^2 \sin^2(\pi k/M) \cos^2(\pi k/M) P_k/P_1$
	\end{itemize}
\end{frame}

\begin{frame}
	\begin{figure}
		\centering
		\includegraphics[width=7cm, height=8cm]{Image1}
	\end{figure}
\end{frame}

\begin{frame}
	\frametitle{Analysis}
	\begin{itemize}
			\item Features that we considered to compare against our model include the following:
			\begin{itemize}
					\item Fractional area of the organoid 
					\item K14 Mean
					\item K14 Sum of pixels intensities in the periphery
					\item K14 Sum of pixels intensities in the center
					\item K14 total pixel intensity sum 
			\end{itemize}
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{An Efficient Way to Get Peripheral Pixels}
	\begin{enumerate}
			\item Generate a mask from the boundary
			\item make a disk to be used as a kernel with which to convolve the mask
			\begin{Example}
				A disk with a radius of 3 is:
				\newline
				$k = \begin{bmatrix}
					0 & 0 & 0 & 1 & 0 & 0 & 0 \\
					0 & 1 & 1 & 1 & 1 & 1 & 0 \\
					0 & 1 & 1 & 1 & 1 & 1 & 0 \\
					1 & 1 & 1 & 1 & 1 & 1 & 1 \\
					0 & 1 & 1 & 1 & 1 & 1 & 0 \\
					0 & 1 & 1 & 1 & 1 & 1 & 0 \\
					0 & 0 & 0 & 1 & 0 & 0 & 0
				\end{bmatrix}$
			\end{Example}
	\end{enumerate}
\end{frame}

\begin{frame}
	\begin{figure}
		\centering
		\includegraphics[width=4cm, height=4cm]{Image4}
		\includegraphics[width=4cm, height=4cm]{Image5}
		\includegraphics[width=4cm, height=4cm]{Image6}
		\begin{columns}
		\column{0.5\textwidth}
			radius, $r= 20$. \newline $pixel size \sim 0.5 \mu$ 
		\end{columns}
	\end{figure}
\end{frame}

\begin{frame}
	\begin{figure}
		\frametitle{Small Organoids}
		\centering
		\includegraphics[width=10cm, height=3cm]{Image2}
	\end{figure}
\end{frame}

\begin{frame}
	\begin{figure}
		\frametitle{Large Organoids}
		\centering
		\includegraphics[width=10cm, height=3cm]{Image3}
	\end{figure}
\end{frame}

\begin{frame}
	\centering
	\resizebox{\textwidth}{!}{
	 \begin{tabular}{||c c c c c c c||}
		 \hline
		 Organoids (mouse\# Size) & 1 Small & 1 Large & 2 Small & 2 Large & 3 Small & 3 Large \\ [0.5ex]
		 \hline\hline
		 Fractional Areav($r^2$) & \textbf{0.401} & 0.211 & \textbf{0.518} & 0.239 & \textbf{0.493} & 0.110 \\
		 \hline
		 Peripheral K14($r^2$) & 0.370 & \textbf{0.379} & 0.464 & \textbf{0.339} & 0.333 & \textbf{0.179} \\
		 \hline
		 Centeral K14($r^2$) & 0.174 & 0.187 & 0.337 & 0.093 & 0.251 & 0.013 \\
		 \hline
		 Total K14($r^2$) & 0.204 & 0.205 & 0.361 & 0.110 & 0.264 & 0.019 \\
		 \hline
		 K14 Mean($r^2$) & 0.057 & 0.011 & 0.023 & 0.239 & 0.011 & 0.023 \\ [1ex]
		 \hline
	\end{tabular}
	}
\end{frame}

\begin{frame}
	\frametitle{Discussion}
	\begin{itemize}
			\item Looking at K14 expression in the periphery of the organoids holds some promise
			\item K14 expression in the center of the organoids correlates less with spectral score than peripheral K14 expression 
			\item K14 Mean doesn't seem to contribute much
			\item Using peripheral K14 expression seems to have more significance for large organoids 
			\item Fractional area and peripheral K14 expression give comparable $r^2$ values
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Future Directions}
	\begin{itemize}
			\item Mouse \#4 data seems to be slightly off, so fix it
			\item Establish statistical significance for our hypothesis 
			\item Apply our model on human organoids generated from breast tumors 
			\newline
			...
	\end{itemize}
\end{frame}

\begin{frame}
	\centering
	Thank You
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\begin{frame}
%\frametitle{Template}
%
%\tikzstyle{na} = [baseline=-.5ex]
%
%\begin{itemize}[<+-| alert@+>]
%    \item Coriolis acceleration
%        \tikz[na] \node[coordinate] (n1) {};
%\end{itemize}
%
%% Below we mix an ordinary equation with TikZ nodes. Note that we have to
%% adjust the baseline of the nodes to get proper alignment with the rest of
%% the equation.
%\begin{equation*}
%\vec{a}_p = \vec{a}_o+\frac{{}^bd^2}{dt^2}\vec{r} +
%        \tikz[baseline]{
%            \node[fill=blue!20,anchor=base] (t1)
%            {$ 2\vec{\omega}_{ib}\times\frac{{}^bd}{dt}\vec{r}$};
%        } +
%        \tikz[baseline]{
%            \node[fill=red!20, ellipse,anchor=base] (t2)
%            {$\vec{\alpha}_{ib}\times\vec{r}$};
%        } +
%        \tikz[baseline]{
%            \node[fill=green!20,anchor=base] (t3)
%            {$\vec{\omega}_{ib}\times(\vec{\omega}_{ib}\times\vec{r})$};
%        }
%\end{equation*}
%
%\begin{itemize}[<+-| alert@+>]
%    \item Transversal acceleration
%        \tikz[na]\node [coordinate] (n2) {};
%    \item Centripetal acceleration
%        \tikz[na]\node [coordinate] (n3) {};
%\end{itemize}
%
%% Now it's time to draw some edges between the global nodes. Note that we
%% have to apply the 'overlay' style.
%\begin{tikzpicture}[overlay]
%        \path[->]<1-> (n1) edge [bend left] (t1);
%        \path[->]<2-> (n2) edge [bend right] (t2);
%        \path[->]<3-> (n3) edge [out=0, in=-90] (t3);
%\end{tikzpicture}
%\end{frame}

\bibliography{refs}
\bibliographystyle{apalike}

\end{document}

### 2018-09-30 docs/site_visit/main.tex
populated the newly added files

--- 2018-09-14 docs/lab_meeting_1/main.tex
@@
 \documentclass{beamer} %
-\usetheme{Boadilla}
+% \usetheme{Boadilla}
 \usepackage[latin1]{inputenc}
@@
 
-\title{Tumor Invasive Scores vs. K14 Expression}
-\author{Yohannes Tsehay}
+\usetheme{Warsaw}
+
+\setbeamercolor{normal text}{fg=yellow,bg=black!90}
+\setbeamercolor{structure}{fg=yellow}
+
+\setbeamercolor{alerted text}{fg=red!85!black}
+
+\setbeamercolor{item projected}{use=item,fg=black,bg=item.fg!35}
+
+\setbeamercolor*{palette primary}{use=structure,fg=structure.fg}
+\setbeamercolor*{palette secondary}{use=structure,fg=structure.fg!95!black}
+\setbeamercolor*{palette tertiary}{use=structure,fg=structure.fg!90!black}
+\setbeamercolor*{palette quaternary}{use=structure,fg=structure.fg!95!black,bg=black!80}
+
+\setbeamercolor*{framesubtitle}{fg=green}
+
+\setbeamercolor*{block title}{parent=structure,bg=black!60}
+\setbeamercolor*{block body}{fg=black,bg=black!10}
+\setbeamercolor*{block title alerted}{parent=alerted text,bg=black!15}
+\setbeamercolor*{block title example}{parent=example text,bg=black!15}
+
+\useoutertheme{split}
+\setbeamertemplate{navigation symbols}{}
+
+\title{Membrane-localized Keratin-14 \\ promotes invasion}
+\author{Yohanes Tsehay \\ \& Andrei Kucharavy}
 %\title{Spectral Analysis}
 \institute{Joel Bader's Lab}
-\date{07/17/2018}
-\logo{\includegraphics[height=1.5cm]{hopkinslogo.jpg}}
+\date{10/04/2018}
+%\logo{\includegraphics[height=1.5cm]{hopkinslogo.jpg}}
+%\logo{\includegraphics[height=1.5cm]{ctd2_overall.png}}
+\titlegraphic{%
+   \includegraphics[width=5cm]{Hopkins_logo_2.png}\hspace*{2.75cm}~%
+   \includegraphics[width=3cm]{ctd2_overall.png}\hspace*{1.75cm}%
+   }
 
@@
 \begin{itemize}
-		\item Background Information
+		% \item Background Information
 		\item Objective
@@
 
-\begin{frame}
-\frametitle{Background}
+% \begin{frame}
+% \frametitle{Background}
 
-\begin{itemize}
-		\item Metastasis is one of the main determinants of patient prognosis 
-		\item Mortality is often due to systemic spread of tumor and not in situ proliferation
-		\begin {Example}
-		5-year survival rate for invasive breast cancer at diagnosis is:
-		\begin {itemize}
-	\item 99\% for patient with \alert{local tumors}
-	\item 85\% for patients with \alert{regional spread}
-	\item 26\% for those with \alert{tumors that have spread to distance organs} \cite{tarver2012cancer}
-		\end {itemize}
-		\end {Example}
-		\item Currently, the molecular mechanism of metastasis is not well understood
-		\item Neoplastic drug interventions mostly target proliferation, not metastatic transformation
-\end{itemize}
+% \begin{itemize}
+% 		\item Metastasis is one of the main determinants of patient prognosis 
+% 		\item Mortality is often due to systemic spread of tumor and not in situ proliferation
+% 		\begin {Example}
+%		5-year survival rate for invasive breast cancer at diagnosis is:
+%		\begin {itemize}
+%	\item 99\% for patient with \alert{local tumors}
+%	\item 85\% for patients with \alert{regional spread}
+%	\item 26\% for those with \alert{tumors that have spread to distance organs} \cite{tarver2012cancer}
+%		\end {itemize}
+%		\end {Example}
+%		\item Currently, the molecular mechanism of metastasis is not well understood
+%		\item Neoplastic drug interventions mostly target proliferation, not metastatic transformation
+%\end{itemize}
 
-\end{frame}
+% \end{frame}
 
@@
 \begin{frame}
-	\frametitle{Related Research Work and Current Developments}
+	\frametitle{Phenotype quantification allows us to pull out the molecular correlates}
 	\begin{itemize}
-			\item A quantitative model to study and characterize metastasis has yet to be developed
-			\item \cite{shamir2014twist1} challenge the epithelial-to-mesenchymal transition requirement for metastasis, and instead, provide evidence in support of a model based on Twist1 induced dissemination of cytokeratin positive epithelial cells
-			\item \cite{cheung2016polyclonal} demonstrated that tumor cells can invade and metastasize in clusters challenging the single-cell/single-metastasis model
-			\item They further study how Keratin 14, a known molecular biomarker for metastasis, expressing cells intiate and complete the metastatic process 
+		\item Invasivenes quantification allows us to calculate the genetic contribution of individual genes
+		\begin{itemize}
+				\item Quantitive characterization allows us to detect even minor contributors
+				\item Quantification of phenotype allows us to calculate the interaction between different genes
+				\item The fine-grainness of the quantification allows us to perform genetic correlation at the genome scale
+		\end{itemize}
+	\end{itemize}
+\end{frame}
+
+\begin{frame}
+	\frametitle{Why we use Keratin 14 as a proof of expression?}
+	\begin{itemize}
+			\item Keratin 14 is a know biomolecular marker for metastasis
+			\item {[Shamir ..
+Bader Ewald 2014]} challenge the epithelial-to-mesenchymal transition requirement for metastasis, and instead, provide evidence in support of a model based on Twist1 induced dissemination of cytokeratin positive epithelial cells
+			\item {[Cheung .. Bader Ewald 2016]} demonstrated that tumor cells only can invade and metastasize in clusters
+			\item in the same paper, Cheung et al. suggested Keratin 14-associated pathways are key regulators of metastasis
 	\end{itemize}
@@
 	\frametitle{Project Objective}
-		The first aim of the project will be to test the hypothesis that K14 is directly correlated with invasiveness versus the alternative hypothesis that organoid size drives both K14 expression and invasion
+	\begin{itemize}
+		\item We will test whether K14 is correlated with invasiveness:
+		\begin{enumerate}
+			\item Total K14 
+			\item Peripheral K14
+			\item Central K14
+		\end{enumerate}
+	\end{itemize}
 \end{frame}
@@
 			\item The organoids were imaged using differential interference contrast (DIC) microscopy
-			\item The images were manually traced using \alert{$ImageJ$} to define organoid boundaries
+			\item The images were manually traced using \textsc{ImageJ} to define organoid boundaries
 			\item corresponding K14 images are available
@@
 
+% \begin{frame}
+% 	\frametitle{Our Computer Model (Spectral Power)}
+%	\begin{itemize}
+%		\item the manually traced boundary is defined by a pair of points \(\{x_v, y_v\}\) for $p \in [0, P-1]$, where $P$ is the total number of points
+%		\item First the overall length $L$ was calculated
+%		\item $L = \sum_{v=1}^{V-1} \sqrt{(x_v - x_{v-1})^2 + (y_v - y_{v-1})^2}$
+%		\item Next, an equally spaced grid was defined with distance $L/M$ between adjacent points, where $M=128$
+%		\item Then, linear interpolation was used to generate a new boundary with equally spaced points \(\{x_j, y_j\}\), where $j \in \{0,1,...,M-1\}$  
+%	\end{itemize}
+% \end{frame}
+
+%\begin{frame}
+%	\frametitle{Fourier Transform of the edge shape}
+%	\begin{itemize}
+%			\item Then, a fast Fourier transform on the newly generated boundary is performed according to:
+%			\newline
+%			$\hat{x}_k = \sum_{j=0}^{M-1} e^{-2\pi ijk/M} x_j$ 
+%			\newline
+%			$\hat{y}_k = \sum_{j=0}^{M-1} e^{-2\pi ijk/M} y_j$ 
+%			\item where $k \in \{0,1,...,M/2+1\}$
+%	\end{itemize}
+%\end{frame}
+
 \begin{frame}
-	\frametitle{Our Computer Model (Spectral Power)}
-	\begin{itemize}
-		\item the manually traced boundary is defined by a pair of points \(\{x_v, y_v\}\) for $p \in [0, P-1]$, where $P$ is the total number of points
-		\item First the overall length $L$ was calculated
-		\item $L = \sum_{v=1}^{V-1} \sqrt{(x_v - x_{v-1})^2 + (y_v - y_{v-1})^2}$
-		\item Next, an equally spaced grid was defined with distance $L/M$ between adjacent points, where $M=128$
-		\item Then, linear interpolation was used to generate a new boundary with equally spaced points \(\{x_j, y_j\}\), where $j \in \{0,1,...,M-1\}$  
-	\end{itemize}
+	\frametitle{Fourier Transform reminder}
+	\begin{figure}
+		\centering
+		\includegraphics[width=7cm]{FFT-Time-Frequency-View.png}
+	\end{figure}
 \end{frame}
 
-\begin{frame}
-	\begin{itemize}
-			\item Then, a fast Fourier transform on the newly generated boundary is performed according to:
-			\newline
-			$\hat{x}_k = \sum_{j=0}^{M-1} e^{-2\pi ijk/M} x_j$ 
-			\newline
-			$\hat{y}_k = \sum_{j=0}^{M-1} e^{-2\pi ijk/M} y_j$ 
-			\item where $k \in \{0,1,...,M/2+1\}$
-	\end{itemize}
-\end{frame}
+% \begin{frame}
+%	\frametitle{Spectral Power}
+%	\begin{itemize}
+%			\item The spectral power $P_k$ is given by:
+%			\newline
+%			$P_k = |\hat{x}_k|^2 + |\hat{y}_k|^2$
+%			\newline
+%			\item where $k \in \{0,1,...,M/2+1\}$
+%			\item $P_0$ is the center and $P_1$ is used to normalize the total power given by:
+%			\newline
+%			$P_{total} = \sum_{k=2}^{M/2+1} P_k/P_1$
+%			\item this produces a spectral power that is scale invariant in addition to being transilation and rotation invariant. 
+%			\item we use a slightly more comples formula to smooth out the artifacts:
+%			\newline
+%			$w \equiv \sum_{k=2}^{M/2} (M/\pi)^2 \sin^2(\pi k/M) \cos^2(\pi k/M) P_k/P_1$
+%	\end{itemize}
+% \end{frame}
+
+%\begin{frame}
+%	\begin{itemize}
+%			\item Means and parametric derivative transforms are estimated
+%			\item This is done to smooth out artifacts in the boundary 
+%			\item The transform for $\bar{x}_{j\prime} \equiv (x_{j\prime+1/2} + x_{j\prime-1/2})/2$ is: 
+%			\newline
+%			$\hat{\bar{x}}_k = \cos(\pi k/M)\hat{x}$ 
+%			\newline
+%			\item The transform for $\dot{x}$ is: 
+%			\newline
+%			$\hat{\dot{x}} = (iM/\pi)\sin(\pi k/M)\hat{x}$
+%			\item Therefore, the final weighted spectral power becomes:
+%			\newline
+%			$w \equiv \sum_{k=2}^{M/2} (M/\pi)^2 \sin^2(\pi k/M) \cos^2(\pi k/M) P_k/P_1$
+%	\end{itemize}
+%\end{frame}
 
 \begin{frame}
-	\begin{itemize}
-			\item The spectral power $P_k$ is given by:
-			\newline
-			$P_k = |\hat{x}_k|^2 + |\hat{y}_k|^2$
-			\newline
-			\item where $k \in \{0,1,...,M/2+1\}$
-			\item $P_0$ is the center and $P_1$ is used to normalize the total power given by:
-			\newline
-			$P_{total} = \sum_{k=2}^{M/2+1} P_k/P_1$
-			\item this produces a spectral power that is scale invariant in addition to being transilation and rotation invariant. 
-	\end{itemize}
-\end{frame}
-
-\begin{frame}
-	\begin{itemize}
-			\item Means and parametric derivative transforms are estimated
-			\item This is done to smooth out artifacts in the boundary 
-			\item The transform for $\bar{x}_{j\prime} \equiv (x_{j\prime+1/2} + x_{j\prime-1/2})/2$ is: 
-			\newline
-			$\hat{\bar{x}}_k = \cos(\pi k/M)\hat{x}$ 
-			\newline
-			\item The transform for $\dot{x}$ is: 
-			\newline
-			$\hat{\dot{x}} = (iM/\pi)\sin(\pi k/M)\hat{x}$
-			\item Therefore, the final weighted spectral power becomes:
-			\newline
-			$w \equiv \sum_{k=2}^{M/2} (M/\pi)^2 \sin^2(\pi k/M) \cos^2(\pi k/M) P_k/P_1$
-	\end{itemize}
-\end{frame}
-
-\begin{frame}
+	\frametitle{Example}
 	\begin{figure}
 		\centering
-		\includegraphics[width=7cm, height=8cm]{Image1}
+		\includegraphics[height=8cm]{fig1_CTN010.pdf}
 	\end{figure}
@@
 \begin{frame}
+
+		\frametitle{Convolution}
+\begin{description}
+	\item	
 	\begin{figure}	
 		\centering
-		\includegraphics[width=4cm, height=4cm]{Image4}
-		\includegraphics[width=4cm, height=4cm]{Image5}
-		\includegraphics[width=4cm, height=4cm]{Image6}
+		\includegraphics[height=4cm]{RiverTrain-ImageConvDiagram}  \hspace*{4cm}
+	\end{figure}
+	\item $ (f*g)[i, j] = \sum_{k=minW_{kernel}}^{maxW_{kernel}}\sum_{l=minH_{kernel}}^{maxH_{kernel}} f[i-k, j-l]g[k, l] $
+\end{description}
+\end{frame}
+
+\begin{frame}
+	\frametitle{Convolution for efficient organoid segmentation}
+	\begin{figure}
+		\centering
+		\includegraphics[width=5cm]{Border}
+		\includegraphics[width=5cm]{convolved_array}
+		\includegraphics[width=3.5cm]{internal_map}
+		\includegraphics[width=3.5cm]{inner_border}
+		\includegraphics[width=3.5cm]{internal_area}
 		\begin{columns}
 		\column{0.5\textwidth}
-			radius, $r= 20$. \newline $pixel size \sim 0.5 \mu$ 
+			radius, $r= 20$ pixel size $\sim 0.5 \mu$ 
 		\end{columns}
@@
 \begin{frame}
+	\frametitle{Peripheral K14 expression correlates with invasive potential}
 	\begin{figure}		
-		\frametitle{Small Organoids}
 		\centering
-		\includegraphics[width=10cm, height=3cm]{Image2}
+		%\includegraphics[width=4cm]{Corr_size}
+		\includegraphics[height=5cm]{Corr_K14}
+		%\includegraphics[width=4cm]{Corr_K14_central}
+		\includegraphics[height=5cm]{Corr_K14_mean}
 	\end{figure}
@@
 	\begin{figure}
-		\frametitle{Large Organoids}
-		\centering
-		\includegraphics[width=10cm, height=3cm]{Image3}
-	\end{figure}
-\end{frame}
-
-\begin{frame}
+		\frametitle{Peripheral K14 explains correlates with invasive potential the best}
 		\centering
 		\resizebox{\textwidth}{!}{
-	 \begin{tabular}{||c c c c c c c||}
+		 \begin{tabular}{||c c c c||}
 			\hline
-		 Organoids (mouse\# Size) & 1 Small & 1 Large & 2 Small & 2 Large & 3 Small & 3 Large \\ [0.5ex]
+			 & \multicolumn{3}{|c|}{$r^2$ by mouse} \\
+			 \hline
+			 Organoids (mouse\#) & 1 & 2 & 3  \\ [0.5ex]
 			 \hline\hline
-		 Fractional Areav($r^2$) & \textbf{0.401} & 0.211 & \textbf{0.518} & 0.239 & \textbf{0.493} & 0.110 \\
+			  \textbf{Peripheral sum K14} & \textbf{0.39} & \textbf{0.43} & \textbf{0.29} \\
 			 \hline
-		 Peripheral K14($r^2$) & 0.370 & \textbf{0.379} & 0.464 & \textbf{0.339} & 0.333 & \textbf{0.179} \\
+			 Centeral sum K14 & 0.21 & 0.19 & 0.11 \\
 			 \hline
-		 Centeral K14($r^2$) & 0.174 & 0.187 & 0.337 & 0.093 & 0.251 & 0.013 \\
+			 Entire sum K14 & 0.22 & 0.22 & 0.12 \\
 			 \hline
-		 Total K14($r^2$) & 0.204 & 0.205 & 0.361 & 0.110 & 0.264 & 0.019 \\
-		 \hline
-		 K14 Mean($r^2$) & 0.057 & 0.011 & 0.023 & 0.239 & 0.011 & 0.023 \\ [1ex]
+%			 K14 Mean & 0.02 & 0.04 & 0.03 \\ [1ex]
+%			 \hline
+			Size & 0.27 & 0.33 & 0.27 \\
 			 \hline
@@
 		}
+	\end{figure}
 \end{frame}
@@
 	\begin{itemize}
-			\item Looking at K14 expression in the periphery of the organoids holds some promise
+			\item Looking at K14 expression in the periphery of the organoids is promising
 			\item K14 expression in the center of the organoids correlates less with spectral score than peripheral K14 expression 
@@
 	\begin{itemize}
-			\item Mouse \#4 data seems to be slightly off, so fix it
-			\item Establish statistical significance for our hypothesis 
+			% \item Mouse \#4 data seems to be slightly off, so fix it
+			% \item Establish statistical significance for our hypothesis 
 			\item Apply our model on human organoids generated from breast tumors 
 			\newline
-			...
 	\end{itemize}
@@
 \begin{frame}
-	\centering
-	Thank You
+ 	\frametitle{Thank you!}
+	\begin{itemize}
+			% \item Mouse \#4 data seems to be slightly off, so fix it
+			% \item Establish statistical significance for our hypothesis 
+			\item Joel Bader
+			\item Joel Bader lab members
+			\newline
+			\item Andrew Ewald
+			\item Veena Padamanaban (data)
+			\item Andrew Ewald members
+			\newline
+			\item Cancer Target Discovery and Development 
+	\end{itemize}
 \end{frame}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\bibliography{refs}
-\bibliographystyle{apalike}
+% \bibliography{refs}
+% \bibliographystyle{apalike}
 

### 2018-09-30 src/autoveena.py

@@ -159,12 +159,12 @@ def get_interpolate(points, contour_in, contour_out):
     return ret
 
 def get_area(points):
-    n = len(points) # of corners
+    n = len(points)  # of corners
     area = 0.0
     for i in range(n):
         j = (i + 1) % n
-        area += points[i,0] * points[j,1]
-        area -= points[j,0] * points[i,1]
+        area += points[i, 0] * points[j, 1]
+        area -= points[j, 0] * points[i, 1]
     area = abs(area) / 2.0
     return area
 

### 2018-09-30 src/convolution_demo.py

@@ -1,0 +1,108 @@
+from csv import reader as csv_reader
+import os
+from matplotlib import pyplot as plt
+import numpy as np
+from skimage.morphology import disk
+from skimage.draw import line as draw_line
+from skimage.segmentation import watershed
+from scipy.ndimage.filters import convolve
+from scipy.ndimage import label
+from PIL import Image
+from skimage.color import rgb2gray
+
+
+source = 'C:\Users\Andrei\Dropbox\Andrei\Data_Final\PyMT\XY\mouse_2_Day5'
+source_2 = 'C:\Users\Andrei\Dropbox\Andrei\Data_Final\PyMT\Images\mouse_2_Day5'
+
+for fle in os.listdir(source):
+    print os.path.join(source, fle)
+    with open(os.path.join(source, fle)) as coordinates_source:
+        reader = csv_reader(coordinates_source, delimiter='\t')
+        xy = []
+        first_line = reader.next()
+        xy.append(first_line)
+        for line in reader:
+            xy.append(line)
+        xy.append(first_line)
+
+        xy = np.array(xy).astype(np.float)*2 - 16
+        xy = xy.astype(np.int)
+
+        base_array = np.zeros((1388, 1040))
+
+        for i in range(0, xy.shape[0]-1):
+            rr, cc = draw_line(xy[i, 0], xy[i, 1], xy[i+1, 0], xy[i+1, 1])
+            base_array[rr, cc] = 1
+
+        im = Image.open(os.path.join(source_2, fle)[:-3]+'tif')
+        im = np.array(im)
+        # plt.imshow(im)
+        # plt.show()
+
+        dic = rgb2gray(im[:, :1388])
+        k14 = rgb2gray(im[:, 1388:])
+
+        plt.imshow(dic, cmap='Greys')
+        plt.axis('off')
+        plt.savefig("DIC.png", bbox_inches='tight')
+        # plt.savefig("test.png", bbox_inches='tight')
+
+        plt.imshow(k14, cmap='Greens')
+        plt.axis('off')
+        # plt.show()
+        plt.savefig("K14.png", bbox_inches='tight')
+
+        plt.imshow(dic, cmap='Greys')
+        plt.imshow(k14, cmap='Greens', alpha=0.5)
+
+        plt.imshow(dic, cmap='Greys')
+        plt.imshow(k14, cmap='Greens', alpha=0.5)
+
+        plt.plot(xy[:, 0], xy[:, 1])
[…]

### 2018-09-30 src/multilevel_regression.py

@@ -1,0 +1,121 @@
+from csv import reader as csv_reader
+import numpy as np
+from matplotlib import pyplot as plt
+from scipy import stats
+
+mouse_data_files = [
+    '../experiments/PyMT_Final/mouse_1_Day5/mouse_1_Day5.txt',
+    '../experiments/PyMT_Final/mouse_2_Day5/mouse_2_Day5.txt',
+    '../experiments/PyMT_Final/mouse_3_Day5/mouse_3_Day5.txt']
+
+
+def parse_data_summary(file_location):
+    data_table = []
+    with open(file_location, 'rb') as source:
+        reader = csv_reader(source, delimiter='\t')
+        header = reader.next()
+        for line in reader:
+            data_table.append(line)
+    return np.array(data_table).astype(np.float)
+
+
+def analysis_loop(data_table):
+
+    def perform_regression(col_1, col_2):
+        slope, intercept, r_value, p_value, std_err = stats.linregress(col_1, col_2)
+
+        return r_value**2, p_value
+
+    headers = ['ID',
+               'Invasion',
+               'Size',
+               'K14 Peripheral Pixels Sum',
+               'K14 Central Pixels Sum',
+               'K14 Entire Sum',
+               'K14 Entire Mean']
+
+    r2_matrix = np.zeros((5, 5))
+
+    exp_var_matrix = np.zeros((5, 5))
+
+
+    base_var = np.var(data_table[:, 1])
+
+    for i in range(2, 7):
+        slope_1, intercept_1, r_value_1, p_value_1, std_err_1 = stats.linregress(data_table[:, i],
+                                                                       data_table[:, 1])
+        remaining_variance = data_table[:, 1] - intercept_1 - data_table[:, i]*slope_1
+        explained_variance = (1 - np.var(remaining_variance) / base_var) * 100
+        print '\t%s: r2: %.2f, p_val: %.2f, rem var: %.2f %%' % (headers[i],
+                                                              r_value_1**2,
+                                                              p_value_1,
+                                                              explained_variance)
+
+        r2_matrix[i-2, i-2] = r_value_1**2
+        exp_var_matrix[i-2, i-2] = explained_variance
+
+        for j in range(2, 7):
+            if i != j:
+                slope_2, intercept_2, r_value_2, p_value_2, std_err_2 = stats.linregress(
+                    data_table[:, j],
+                    remaining_variance)
[…]

### 2018-09-30 src/multilevel_regression.py
added the regression results for the C1tag mice

@@ -8,6 +8,11 @@ mouse_data_files = [
     '../experiments/PyMT_Final/mouse_2_Day5/mouse_2_Day5.txt',
     '../experiments/PyMT_Final/mouse_3_Day5/mouse_3_Day5.txt']
 
+mouse_data_files = [
+    '../experiments/C31T_Final/mouse_1_Day5/mouse_1_Day5.txt',
+    '../experiments/C31T_Final/mouse_2_Day5/mouse_2_Day5.txt',
+    '../experiments/C31T_Final/mouse_3_Day5/mouse_3_Day5.txt',
+    '../experiments/C31T_Final/mouse_4_Day5/mouse_4_Day5.txt']
 
 def parse_data_summary(file_location):
     data_table = []
@@ -106,7 +111,7 @@ def analysis_loop(data_table):
                 plt.ylabel(headers[1], fontsize=16)
 
                 plt.tight_layout()
-                plt.show()
+                # plt.show()
 
     np.set_printoptions(precision=2, suppress=True)
     print r2_matrix

### 2018-10-01 experiments/run_20180619/run.sh
Finalized the PyMT and C31T experiments -The outputs now include K14 means for both the peripheral and central pixels -Summary plot generated on ellipse plots also include all variables -plot layout fixed, plotting 10 organoids per page instead of all organoids on one page -Deleted old run folders under experiment

@@ -1,29 +1,0 @@
-time python ./ibis2d.py --veenafile Veena_Orig.txt --matchfile Veena_Matches.txt --dic_orig ../IMAGES_Tumor_Day6_DIC_K14_original --outdir ../autoveena_2017_12_14 --coords ../COORDS_VALID --nfft 256
-
-#time python ./ibis2d.py --veenafile Veena_Orig.txt --matchfile Veena_Matches.txt --invasionfile invasion_table.txt --k14file k14_table.txt --dic_orig ../IMAGES_Tumor_Day6_DIC_K14_original --outdir ../autoveena_2017_10_23 --coords ../COORDS_VALID --nfft 256
-
-#time python ./ibis2d.py --invasionfile invasion_table.txt --dic_orig ../IMAGES_Tumor_Day6_DIC_K14_original --outdir ../autoveena_2017_10_23 --coords ../COORDS_VALID --nfft 256
-
-#time python ./ibis2d.py --veenafile Veena_Orig.txt --invasionfile invasion_table.txt --dic_orig ../IMAGES_Tumor_Day6_DIC_K14_original --dic_renamed ../IMAGES_Tumor_Day6_DIC_renamed --outdir ../autoveena_2017_10_23 --coords ../COORDS_VALID --images ../IMAGES_VALID --nfft 256 --recalculate n --thumbnails n --thermometers n
-
-#time python ./ibis2d.py --coords ../COORDS_VALID --images ../IMAGES_VALID --outdir ../analysis_2017_07_02_zscore --nfft 256 --recalculate n --thumbnails n --thermometers y
-
-
-# time python ./ibis2d.py --coords ../COORDS_106 --images ../IMAGES_VALID --outdir ../analysis_106 --nfft 256 --recalculate n --thumbnails y --thermometers n
-
-
-#time python ./ibis2d.py --coords ../COORDS_VALID --outdir ../analysis_2017_06_28 --nfft 256 --recalculate y
-
-#time python ./ibis2d.py --coords ../COORDS_CIRCLE --outdir ../analysis_circle --nfft 256 --recalculate y --thumbnails n
-
-#time python ./ibis2d.py --coords ../COORDS_106 --outdir ../analysis_106 --nfft 256 --recalculate y --thumbnails n
-
[…]

### 2018-10-01 src/generate_summary_plots.py

@@ -101,14 +101,15 @@ def main():
     rows = len(files)
 
     for f in files:
-        plt.figure(figsize=(17,7))
+        plt.figure(figsize=(25,10))
         plt.suptitle(f.split('/')[-1])
         data = read_file(f)
-        sps = [151, 152, 153, 154, 155]
-        for (sp, xname) in zip( sps, ('K14 Sum Peripheral Pixels', 'Fractional Area', 'K14 Sum Central Pixels', 'K14 Total Sum', 'K14 Mean') ):
+        sps = [241, 242, 243, 244, 245, 246, 247]
+        for (sp, xname) in zip( sps, ('K14 Sum Peripheral Pixels', 'Fractional Area', 'K14 Sum Central Pixels', 'K14 Total Sum', 'K14 Total Mean', 'K14 Peripheral Mean', 'K14 Central Mean') ):
             plot_ellipse(sp, data[xname], data['Invasion'], xname, 'Invasion')
         pdf.savefig()
         plt.close()
+    plt.tight_layout()
     pdf.close()             
     
     return None

### 2018-10-01 src/ibis2d_mine.py

@@ -1509,7 +1509,7 @@ def calc_inv_vs_k14(args):
         new_table[i] = dict()
     new_fields = ['invasion_spectral', 'invasion_ff',
                   'size_area', 'size_perimeter', 'size_npixel', 'size_frac',
-                  'k14_mean', 'k14_sum', 'k14_sum_edge', 'k14_sum_center',
+                  'k14_mean', 'k14_mean_edge', 'k14_mean_center', 'k14_sum', 'k14_sum_edge', 'k14_sum_center',
                   'tag_photometric', 'tag_color', 'tag_scale']
     for k in new_table:
         for f in new_fields:
@@ -1540,6 +1540,8 @@ def calc_inv_vs_k14(args):
     sumpower_list = [ ]
     sumpowerksq_list = [ ]
     k14mean_list = [ ]
+    k14_edge_mean_list = [ ]
+    k14_center_mean_list = [ ]
     k14sum_list = [ ]
     k14sum_edge_list = [ ]
     k14sum_center_list = [ ]
@@ -1589,11 +1591,15 @@ def calc_inv_vs_k14(args):
             
             k14sum = np.sum(pixels_inside.ravel())
             k14mean = np.mean(pixels_inside.ravel())
+            k14mean_edge = np.mean(pixels_inside_peripheral_mask.ravel())
+            k14mean_center = np.mean(pixels_inside_central_mask.ravel())
             ninside = len(pixels_inside.ravel())
             ntotal = len(img_k14.ravel())
             # logger.info('%s %d pixels, sum = %f, mean = %f', k, ninside, k14sum, k14mean)
             if (tag_photometric == '1'):
                 k14mean = 255.0 - k14mean
+                k14mean_edge = 255.0 - k14mean_edge
+                k14mean_center = 255.0 - k14mean_center
                 k14sum = (255.0 * ninside) - k14sum
                 k14sum_edge = (255.0 * ninside) - k14sum_edge
                 k14sum_center = (255.0 * ninside) - k14sum_center
@@ -1602,6 +1608,8 @@ def calc_inv_vs_k14(args):
             k14sum_edge = k14sum_edge / float(ntotal * 255)
             k14sum_center = k14sum_center / float(ntotal * 255)
             k14mean = k14mean / 255.0
+            k14mean_edge = k14mean_edge / 255.0
[…]

### 2018-10-25 docs/01_paper/paper.tex
-Added paper template

%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{Membrane-localized Keratin-14 Promotes Invasion\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Princeton University, Princeton NJ 08544, USA \and
Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
\email{lncs@springer.com}\\
\url{http://www.springer.com/gp/computer-science/lncs} \and
ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
\email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Metastasis is the main predictor of outcome for patients with cancer, yet the molecular mechanism driving invasive phenotypes is not well understood. Keratin 14 (K14) is a known molecular biomarker that is correlated with poor outcomes in breast cancer patients. In this study, we apply our automated computer model that quantifies the invasive potential of tumors to characterize K14 expression as it relates to invasion. We test the hypothesis that K14 is directly correlated to invasion versus the alternative hypothesis that size is the main predictor. We used two different transgenic mice as our breast cancer tumor models. Organoids were generated from these mice, and each organoid had a corresponding differential interference contrast image, K14 image, and an invasive potential score generated using our automated system. The parameters assessed include the following: entire K14 expression, peripheral K14 expression (edges of the organoid), central K14 expression (center of the organoid), and organoid size. Peripheral K14 expression showed the strongest correlation with invasion scores for both types of transgenic mice. The results suggest that K14 expression in cells located in the periphery may be an important marker of invasion.

\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}
%
%
%
\section{First Section}
\subsection{A Subsection Sample}
Please note that the first paragraph of a section or subsection is
not indented. The first paragraph that follows a table, figure,
equation etc. does not need an indent, either.

Subsequent paragraphs, however, are indented.

\subsubsection{Sample Heading (Third Level)} Only two levels of
headings should be numbered. Lower level headings remain unnumbered;
they are formatted as run-in headings.

\paragraph{Sample Heading (Fourth Level)}
The contribution should contain no more than four levels of
headings. Table~\ref{tab1} gives a summary of all heading levels.

\begin{table}
\caption{Table captions should be placed above the
tables.}\label{tab1}
\begin{tabular}{|l|l|l|}
\hline
Heading level &  Example & Font size and style\\
\hline
Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
\hline
\end{tabular}
\end{table}

\noindent Displayed equations are centered and set on a separate
line.
\begin{equation}
x + y = z
\end{equation}
Please try to avoid rasterized images for line-art diagrams and
schemas. Whenever possible, use vector graphics instead (see
Fig.~\ref{fig1}).

\begin{figure}
\includegraphics[width=\textwidth]{fig1.eps}
\caption{A figure caption is always placed below the illustration.
Please note that short captions are centered, while long ones are
justified by the macro package automatically.} \label{fig1}
\end{figure}

\begin{theorem}
This is a sample theorem. The run-in heading is set in bold, while
the following text appears in italics. Definitions, lemmas,
propositions, and corollaries are styled the same way.
\end{theorem}
%
% the environments 'definition', 'lemma', 'proposition', 'corollary',
% 'remark', and 'example' are defined in the LLNCS documentclass as well.
%
\begin{proof}
Proofs, examples, and remarks have the initial word in italics,
while the following text appears in normal font.
\end{proof}
For citations of references, we prefer the use of square brackets
and consecutive numbers. Citations using labels or the author/year
convention are also acceptable. The following bibliography provides
a sample reference list with entries for journal
articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
and a homepage~\cite{ref_url1}. Multiple citations are grouped
\cite{ref_article1,ref_lncs1,ref_book1},
\cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}
\bibitem{ref_article1}
Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)

\bibitem{ref_lncs1}
Author, F., Author, S.: Title of a proceedings paper. In: Editor,
F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
Springer, Heidelberg (2016). \doi{10.10007/1234567890}

\bibitem{ref_book1}
Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
Location (1999)

\bibitem{ref_proc1}
Author, A.-B.: Contribution title. In: 9th International Proceedings
on Proceedings, pp. 1--2. Publisher, Location (2010)

\bibitem{ref_url1}
LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
Oct 2017
\end{thebibliography}
\end{document}

### 2018-10-25 docs/01_paper/paper.tex
Updates from ShareLaTeX

@@
 \usepackage{graphicx}
+\usepackage{comment}
 % Used for displaying a sample figure. If possible, figure files should
@@
 %
-\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
+\author{First Author \inst{1}\orcidID{0000-1111-2222-3333} \and
 Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
@@
 %
-\institute{Princeton University, Princeton NJ 08544, USA \and
-Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
-\email{lncs@springer.com}\\
-\url{http://www.springer.com/gp/computer-science/lncs} \and
-ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
-\email{\{abc,lncs\}@uni-heidelberg.de}}
+\institute{Johns Hopkins University
+\url{http://www} \and
+Other\\
+\email{\{bla,blu\}@jhu.edu}}
 %
@@
 
-\keywords{First keyword  \and Second keyword \and Another keyword.}
+\keywords{Tumor Invasion  \and Keratin 14 \and ...}
 \end{abstract}
@@
 %
-\section{First Section}
-\subsection{A Subsection Sample}
-Please note that the first paragraph of a section or subsection is
-not indented. The first paragraph that follows a table, figure,
-equation etc. does not need an indent, either.
+\section{Introduction}
 
-Subsequent paragraphs, however, are indented.
+\section {Methods}
 
-\subsubsection{Sample Heading (Third Level)} Only two levels of
-headings should be numbered. Lower level headings remain unnumbered;
-they are formatted as run-in headings.
+\subsection{Databse}
 
-\paragraph{Sample Heading (Fourth Level)}
-The contribution should contain no more than four levels of
-headings. Table~\ref{tab1} gives a summary of all heading levels.
+\subsection{Spectral Analysis}
 
+\subsubsection{}
+
+\section{Results}
+
+\section{Discussion}
+
+\section{Conclusion}
+
+\paragraph{}
+
+\begin{comment}
 \begin{table}
@@
 \end{thebibliography}
+
+\end{comment}
+
 \end{document}

### 2018-11-15 docs/01_paper/paper.tex
Added mouse #4 results for site_visit presentation.
Added Database section

@@
 \usepackage{comment}
+\usepackage{xcolor}
 % Used for displaying a sample figure. If possible, figure files should
@@
 We test the hypothesis that K14 is directly correlated to invasion versus the alternative hypothesis that size is the main predictor.
-We used two different transgenic mice as our breast cancer tumor models.
+We used two different transgenic mice (PyMT and C3(1)-Tag) as our breast cancer tumor models.
 Organoids were generated from these mice, and each organoid had a corresponding differential interference contrast image, K14 image, and an invasive potential score generated using our automated system.
@@
 
-\keywords{Tumor Invasion  \and Keratin 14 \and ...}
+\keywords{Metastasis \and Tumor Invasion \and Keratin 14 \and Spectral Analysis \and ...}
 \end{abstract}
@@
 
+Alternative title: Morphological features of organoid invasion are correlated to membrane-localized Keratin-14 expression
+
+\textcolor{blue}{
+\begin{itemize}
+    \item Biology intro (what is our audience). The two different mice models.
+    \item How K14 expression is related to metastasis.
+    \item The use of image analysis for feature extraction, lit review.
+    \item Why spectral score is a good measure for invasion potential.
+    \item Paper outline
+\end{itemize}
+}
+
+Metastasis stats.
+
+What are organoids.
+
+Quantitative phenotypes.
+
+Hypothesis: a) K14 expression is correlated with organoid invasion.\\
+b) organoid size is correlated with invasion score.
+
+Research questions:
+
 \section {Methods}
 
-\subsection{Databse}
+Fig. 0: Make figure showing the 'pipeline'.
+
+\textcolor{blue}{
+\begin{itemize}
+    \item Experimental protocol. Ask Veena to write this part.\\ 
+        100-300 organoids from 4 mice.
+    \item Image acquisition and organoid periphery. Veena.\\
+        Use ImageJ to mark the periphery of the organoids from DCI microscop images.
+    \item Image segmentation. Andrei to write about convolution kernel.
+    \item Spectral score. Reference Joel's paper. Disclose scripts?
+\end{itemize}
+}
+
+\subsection{Database}
+
+ A total of 4 PyMT and 4 C31T mice were used to generate a total of \{\} organoids, which were then cultured in collagen I gels for 5 days.
+At day 5, they were imaged, an average of 16 per sample.
+Differential interference contrast (DIC) microscopy yielded 1040$\times$1388 pixel images.
+Microscope optics defined a resolution of 0.51190476 $\mu$m per pixel, corresponding to a 532.4$\times$710.5 $\mu$m field of view.
+Images were manually tracked in {\sc ImageJ} \cite{Schneider:2012ui} to define the organoid boundaries as pairs of points $\{x_v,y_v\}$ for $v \in [0,V-1]$.
+The total number of points $V$ depended on the manual tracking, and the spacing between adjacent points was similarly variable.
 
@@
 
+Start adding figures here.\\
+Q: Are we keeping the large vs. small organoids?
+Q: should this be split into PyMT section and C31Tag section?
+
+Fig. 1: show each step in the pipeline from DCI to spectral score for 2 organoids (one with low spectral score and one with high spectral score).
+
+Fig. 2: show figures for the convolution kernel used to get peripheral K14 expression.
+
+Fig. 3: Correlation plots PyMT
+
+Fig. 4: Correlation plots C31Tag
+
+Table 1: Summary statistics
+
 \section{Discussion}
+
+Future directions: Test our method on Patient derived organoids, PDOs.\\
+Does organoid invasion score correlate with patient outcome?
 
@@
 
-\paragraph{}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{comment}
@@
 %
-\begin{thebibliography}{8}
-\bibitem{ref_article1}
-Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)
-
-\bibitem{ref_lncs1}
-Author, F., Author, S.: Title of a proceedings paper. In: Editor,
-F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
-Springer, Heidelberg (2016). \doi{10.10007/1234567890}
-
-\bibitem{ref_book1}
-Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
-Location (1999)
-
-\bibitem{ref_proc1}
-Author, A.-B.: Contribution title. In: 9th International Proceedings
-on Proceedings, pp. 1--2. Publisher, Location (2010)
-
-\bibitem{ref_url1}
-LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
-Oct 2017
-\end{thebibliography}
 
@@
 
+\begin{thebibliography}{8}
+
+\bibitem{Schneider:2012ui}
+Schneider CA, Rasband WS, Eliceiri KW.
+\newblock {NIH Image to ImageJ: 25 years of image analysis.}
+\newblock Nature methods. 2012;9(7):671--675.
+
+\end{thebibliography}
+
 \end{document}

### 2018-11-15 src/ibis2d_mine.py
Added a way to generate figures and added figure 1

@@ -1842,6 +1842,103 @@ def cluster(args):
     plt.close()
     return None
 
+def generate_figures(args):
+
+    orig_dir = args.images
+    xy_dir = args.coords
+    nfft = args.nfft
+    figurename=args.outdir
+    
+    filenames = os.listdir(xy_dir)
+    organoids = [f.split('.')[0] for f in filenames if not f.startswith('.')]
+            
+    plotfile = os.path.join(figurename + '.pdf')
+    pdf = PdfPages(plotfile)
+
+    k_vector = np.arange(1 + (nfft/2)) # since rfft uses only half the range
+    k_sq = k_vector * k_vector # element multiply
+
+    fac = 2.0 * math.pi / float(nfft)
+    facsq = fac * fac
+    smooth = np.exp(-facsq * k_sq)
+    
+    nrow = len(organoids)
+    ncol = 4
+
+    plt.figure(figsize=(25, nrow * ncol))
+    
+    rownum = 0
+
+    for k in organoids:
+        # k14 begin
+        logger.info('... %s', k)
+        
+        xy_file = os.path.join(xy_dir, k + '.txt')
+        (xy_raw, xy_interp, xy_hat, tot_length, area, form_factor, power_norm) = xyfile_to_spectrum(xy_file, nfft)
+        power_norm = power_norm * smooth
+        power_ksq = power_norm * k_sq
+        sumpower = sum(power_norm[2:])
+        sumpowerksq = sum(power_ksq[2:])
+
+        fullpath = os.path.join(orig_dir, k + '.tif')
+        (img_dic, img_k14, scale, tag_photometric, tag_color) = read_image_pair(fullpath)
+        
+        # all the plots
+        rownum += 1
+        i = (rownum - 1) * ncol # plot sequence number starting point
+
+        # K14 image
+        i += 1
+        plt.subplot(nrow, ncol, i)
+        plt.imshow(img_k14)
+        plt.title('K14 Image')
+        #plt.ylabel('%s' % k)
+
+        # DIC image
+        i += 1
+        plt.subplot(nrow, ncol, i)
+        plt.title('DIC Image')
+        plt.imshow(img_dic)
+
+        # boundary from raw points
+        i += 1
+        ax = plt.subplot(nrow, ncol, i)
+        # make sure the path is closed
+        x = list(xy_raw[:,0])
+        y = list(xy_raw[:,1])
+        x.append(x[0])
+        y.append(y[0])
+        xx = [ scale * val for val in x ]
+        yy = [ scale * val for val in y]
[…]

### 2018-12-06 docs/01_paper/paper.tex
Added a way to generate figures and added figure 1
Updates from ShareLaTeX
Added Joel's recommended template

@@
 
-Alternative title: Morphological features of organoid invasion are correlated to membrane-localized Keratin-14 expression
+Alternative title: Morphological features of organoid invasion are correlated with membrane-localized Keratin-14 expression
 
@@
 
+Previous observation from Ewald group about K14 expression.
+
 Hypothesis: a) K14 expression is correlated with organoid invasion.\\
@@
     \item Image acquisition and organoid periphery. Veena.\\
-        Use ImageJ to mark the periphery of the organoids from DCI microscop images.
+        Use ImageJ to mark the periphery of the organoids from DIC microscope images.
     \item Image segmentation. Andrei to write about convolution kernel.
@@
 
-\subsection{Database}
+\subsection{Data acquisition}
 
@@
 \subsection{Spectral Analysis}
+A method described in REF.\\
+Able to distinguish quantitative phenotypes.
 
-\subsubsection{}
+\subsection{Convolution kernel}
+ANDREI
+
+\subsection{Correlation Analysis}
+
+\begin{figure}
+\includegraphics[width=\textwidth]{Image1.pdf}
+\caption{Displays the K14 Image, DIC image, Bounday and spectral power analysis plots for three different organoids.
+\textcolor{red}{Axis font needs to be bigger.
+Y-axis in spectral score should all be the same and we can probably skip column 2.}} \label{fig1}
+\end{figure}
 
 \section{Results}
+
+\begin{table}
+\caption{Peripheral K14 explains correlates with invasive potential the best.}\label{tab1}
+		\centering
+		\resizebox{0.8\textwidth}{!}{
+		 \begin{tabular}{||l c c c c||}
+			\hline
+			 & \multicolumn{4}{|c|}{$r^2$ by mouse} \\
+			 \hline
+			 Organoids (PyMMT mice) & 	1 & 2 & 3 & 4 \\ [0.5ex]
+			 \hline\hline
+			  \textbf{Peripheral sum K14} & \textbf{0.39} & \textbf{0.43} & \textbf{0.29} & \textbf{0.123} \\
+			 \hline
+			 Centeral sum K14 & 0.21 & 0.19 & 0.11 & 0.010 \\
+			 \hline
+			 Entire sum K14 & 0.22 & 0.22 & 0.12 & 0.013 \\
+			 \hline
+%			 K14 Mean & 0.02 & 0.04 & 0.03 \\ [1ex]
+%			 \hline
+			Organoid size & 0.27 & 0.33 & 0.27 & 0.076 \\
+			 \hline
+		\end{tabular}
+		}
+\end{table}
+
+\begin{table}
+\caption{Peripheral K14 explains correlates with invasive potential the best.}\label{tab1}
+		\centering
+		\resizebox{0.8\textwidth}{!}{
+		 \begin{tabular}{||l c c c c||}
+			\hline
+			 & \multicolumn{4}{|c|}{$r^2$ by mouse} \\
+			 \hline
+			 Organoids (C3(1)tag mice) & 1 & 2 & 3 & 4  \\ [0.5ex]
+			 \hline\hline
+			  \textbf{Peripheral sum K14} & \textbf{0.11} & \textbf{0.25} & 0.06 & 0.03 \\
+			 \hline
+			 Centeral sum K14 & 0.01 & 0.03 & 0.06 & 0.00\\
+			 \hline
+			 Entire sum K14 & 0.01 & 0.00 & 0.01 & 0.00\\
+			 \hline
+%			 K14 Mean & 0.02 & 0.04 & 0.03 & xx\\ [1ex]
+%			 \hline
+			Organoid size & 0.07 & 0.01 & \textbf{0.07} &  \textbf{0.06} \\
+			 \hline
+		\end{tabular}
+		}
+\end{table}
 
@@
 \section{Discussion}
-
+We implemented a method to quanitfy the invasive phenotypes organoids derived from two distinct mouse models, namely PyMT and C3(1)tag.\\
+Out of the features we tested, we found that peripheral K14 expression correlated with the invasive phenotype.\\
+Why is this important and/or interesting?\\
 Future directions: Test our method on Patient derived organoids, PDOs.\\

### 2018-12-06 docs/01_paper/paper_2.tex
Added Joel's recommended template

% Template for PLoS
% Version 3.5 March 2018
%
% % % % % % % % % % % % % % % % % % % % % %
%
% -- IMPORTANT NOTE
%
% This template contains comments intended 
% to minimize problems and delays during our production 
% process. Please follow the template instructions
% whenever possible.
%
% % % % % % % % % % % % % % % % % % % % % % % 
%
% Once your paper is accepted for publication, 
% PLEASE REMOVE ALL TRACKED CHANGES in this file 
% and leave only the final text of your manuscript. 
% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
%
%
% There are no restrictions on package use within the LaTeX files except that 
% no packages listed in the template may be deleted.
%
% Please do not include colors or graphics in the text.
%
% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
%
% % % % % % % % % % % % % % % % % % % % % % %
%
% -- FIGURES AND TABLES
%
% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
%
% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
% - Figures should be uploaded separately from your manuscript file. 
% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
% For figure citations, please use "Fig" instead of "Figure".
% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
%
% Tables should be cell-based and may not contain:
% - spacing/line breaks within cells to alter layout or alignment
% - do not nest tabular environments (no tabular environments within tabular environments)
% - no graphics or colored text (cell background color/shading OK)
% See http://journals.plos.org/plosone/s/tables for table guidelines.
%
% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
%
% % % % % % % % % % % % % % % % % % % % % % % %
%
% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
%
% IMPORTANT
% Below are a few tips to help format your equations and other special characters according to our specifications. For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
%
% For inline equations, please be sure to include all portions of an equation in the math environment.  For example, x$^2$ is incorrect; this should be formatted as $x^2$ (or $\mathrm{x}^2$ if the romanized font is desired).
%
% Do not include text that is not math in the math environment. For example, CO2 should be written as CO\textsubscript{2} instead of CO$_2$.
%
% Please add line breaks to long display equations when possible in order to fit size of the column. 
%
% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
%
% When adding superscript or subscripts outside of brackets/braces, please group using {}.  For example, change "[U(D,E,\gamma)]^2" to "{[U(D,E,\gamma)]}^2". 
%
% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
%
% % % % % % % % % % % % % % % % % % % % % % % % 
%
% Please contact latex@plos.org with any questions.
%
% % % % % % % % % % % % % % % % % % % % % % % %

\documentclass[10pt,letterpaper]{article}
\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}

% amsmath and amssymb packages, useful for mathematical formulas and symbols
\usepackage{amsmath,amssymb}

% Use adjustwidth environment to exceed column width (see example table in text)
\usepackage{changepage}

% For commenting
\usepackage{comment}

% Use Unicode characters when possible
\usepackage[utf8x]{inputenc}

% textcomp package and marvosym package for additional characters
\usepackage{textcomp,marvosym}

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}

% Use nameref to cite supporting information files (see Supporting Information section for more info)
\usepackage{nameref,hyperref}

% line numbers
\usepackage[right]{lineno}

% ligatures disabled
\usepackage{microtype}
\DisableLigatures[f]{encoding = *, family = * }

% color can be used to apply background shading to table cells only
\usepackage[table]{xcolor}

% array package and thick rules for tables
\usepackage{array}

% create "+" rule type for thick vertical lines
\newcolumntype{+}{!{\vrule width 2pt}}

% create \thickcline for thick horizontal lines of variable length
\newlength\savedwidth
\newcommand\thickcline[1]{%
  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
  \cline{#1}%
  \noalign{\vskip\arrayrulewidth}%
  \noalign{\global\arrayrulewidth\savedwidth}%
}

% \thickhline command for thick horizontal lines that span the table
\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
\hline
\noalign{\global\arrayrulewidth\savedwidth}}

% Remove comment for double spacing
%\usepackage{setspace} 
%\doublespacing

% Text layout
\raggedright
\setlength{\parindent}{0.5cm}
\textwidth 5.25in 
\textheight 8.75in

% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
% Captions will be left justified
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
\renewcommand{\figurename}{Fig}

% Use the PLoS provided BiBTeX style
\bibliographystyle{plos2015}

% Remove brackets from numbering in List of References
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

% Header and Footer with logo
\usepackage{lastpage,fancyhdr,graphicx}
\usepackage{epstopdf}
%\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
%\setlength{\headheight}{27.023pt}
%\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\today}

%% Include all macros below

\newcommand{\lorem}{{\bf LOREM}}
\newcommand{\ipsum}{{\bf IPSUM}}

%% END MACROS SECTION

\begin{document}
\vspace*{0.2in}

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Membrane-localized Keratin-14 Promotes Invasion} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Name1 Surname\textsuperscript{1,2\Yinyang},
Name2 Surname\textsuperscript{2\Yinyang},
Name3 Surname\textsuperscript{2,3\textcurrency},
Name4 Surname\textsuperscript{2},
Name5 Surname\textsuperscript{2\ddag},
Name6 Surname\textsuperscript{2\ddag},
Name7 Surname\textsuperscript{1,2,3*},
with the Lorem Ipsum Consortium\textsuperscript{\textpilcrow}
\\
\bigskip
\textbf{1} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\textbf{2} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\textbf{3} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\bigskip

% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
% 
% Remove or comment out the author notes below if they aren't used.
%
% Primary Equal Contribution Note
\Yinyang These authors contributed equally to this work.

% Additional Equal Contribution Note
% Also use this double-dagger symbol for special authorship notes, such as senior authorship.
\ddag These authors also contributed equally to this work.

% Current address notes
\textcurrency Current Address: Dept/Program/Center, Institution Name, City, State, Country % change symbol to "\textcurrency a" if more than one current address note
% \textcurrency b Insert second current address 
% \textcurrency c Insert third current address

% Deceased author note
\dag Deceased

% Group/Consortium Author Note
\textpilcrow Membership list can be found in the Acknowledgments section.

% Use the asterisk to denote corresponding authorship and provide email address in note below.
* correspondingauthor@institute.edu

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
Metastasis is the main predictor of outcome for patients with cancer, yet the molecular mechanism driving invasive phenotypes is not well understood. Keratin 14 (K14) is a known molecular biomarker that is correlated with poor outcomes in breast cancer patients. In this study, we apply our automated computer model that quantifies the invasive potential of tumors to characterize K14 expression as it relates to invasion. We test the hypothesis that K14 is directly correlated to invasion versus the alternative hypothesis that size is the main predictor. We used two different transgenic mice (PyMT and C3(1)-Tag) as our breast cancer tumor models. Organoids were generated from these mice, and each organoid had a corresponding differential interference contrast image, K14 image, and an invasive potential score generated using our automated system. The parameters assessed include the following: entire K14 expression, peripheral K14 expression (edges of the organoid), central K14 expression (center of the organoid), and organoid size. Peripheral K14 expression showed the strongest correlation with invasion scores for both types of transgenic mice. The results suggest that K14 expression in cells located in the periphery may be an important marker of invasion.

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
\section*{Author summary}

\linenumbers

% Use "Eq" instead of "Equation" for equation citations.
\section*{Introduction}
%Lorem ipsum dolor sit~\cite{bib1} amet, consectetur adipiscing elit. Curabitur eget porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante cursus gravida non sed sem. Nullam Eq~(\ref{eq:schemeP}) sapien tellus, commodo id velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id.~\cite{bib2} Nunc convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.

Alternative title: Morphological features of organoid invasion are correlated with membrane-localized Keratin-14 expression

\textcolor{blue}{
\begin{itemize}
    \item Biology intro (what is our audience). The two different mice models.
    \item How K14 expression is related to metastasis.
    \item The use of image analysis for feature extraction, lit review.
    \item Why spectral score is a good measure for invasion potential.
    \item Paper outline
\end{itemize}
}

Metastasis stats.

What are organoids.

Quantitative phenotypes.

Previous observation from Ewald group about K14 expression.

Hypothesis: a) K14 expression is correlated with organoid invasion.\\
b) organoid size is correlated with invasion score.

Research questions:

%\begin{eqnarray}
%\label{eq:schemeP}
%	\mathrm{P_Y} = \underbrace{H(Y_n) - H(Y_n|\mathbf{V}^{Y}_{n})}_{S_Y} + \underbrace{H(Y_n|\mathbf{V}^{Y}_{n})- %H(Y_n|\mathbf{V}^{X,Y}_{n})}_{T_{X\rightarrow Y}},
%\end{eqnarray}

\section*{Materials and methods}
\subsection*{Data acquisition}

 A total of 4 PyMT and 4 C31T mice were used to generate a total of \{\} organoids, which were then cultured in collagen I gels for 5 days. At day 5, they were imaged, an average of 16 per sample. Differential interference contrast (DIC) microscopy yielded 1040$\times$1388 pixel images. Microscope optics defined a resolution of 0.51190476 $\mu$m per pixel, corresponding to a 532.4$\times$710.5 $\mu$m field of view. Images were manually tracked in {\sc ImageJ} \cite{Schneider:2012ui} to define the organoid boundaries as pairs of points $\{x_v,y_v\}$ for $v \in [0,V-1]$. The total number of points $V$ depended on the manual tracking, and the spacing between adjacent points was similarly variable.

% For figure citations, please use "Fig" instead of "Figure".
% Nulla mi mi, Fig~\ref{fig1} venenatis sed ipsum varius, volutpat euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, \nameref{S1_Video} vel sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent faucibus semper libero.

% Results and Discussion can be combined.
\section*{Results}
% Nulla mi mi, venenatis sed ipsum varius, Table~\ref{table1} volutpat

\begin{figure}[!h]
\includegraphics[width=\textwidth]{Image1.pdf}
\caption{Displays the K14 Image, DIC image, Bounday and spectral power analysis plots for three different organoids. \textcolor{red}{Axis font needs to be bigger. Y-axis in spectral score should all be the same and we can probably skip column 2.}} 
\label{fig1}
\end{figure}

\begin{table}
\caption{{\bf Peripheral K14 explains correlates with invasive potential the best.}}
\label{tab1}
		\centering
		\resizebox{0.8\textwidth}{!}{
		 \begin{tabular}{||l c c c c||}
			\hline
			 & \multicolumn{4}{|c|}{$r^2$ by mouse} \\
			 \hline
			 Organoids (PyMMT mice) & 	1 & 2 & 3 & 4 \\ [0.5ex]
			 \hline\hline
			  \textbf{Peripheral sum K14} & \textbf{0.39} & \textbf{0.43} & \textbf{0.29} & \textbf{0.123} \\
			 \hline
			 Centeral sum K14 & 0.21 & 0.19 & 0.11 & 0.010 \\
			 \hline
			 Entire sum K14 & 0.22 & 0.22 & 0.12 & 0.013 \\
			 \hline
%			 K14 Mean & 0.02 & 0.04 & 0.03 \\ [1ex]
%			 \hline
			Organoid size & 0.27 & 0.33 & 0.27 & 0.076 \\
			 \hline
		\end{tabular}
		}
\end{table}

\begin{table}
\caption{{\bf Peripheral K14 explains correlates with invasive potential the best.}}
\label{tab1}
		\centering
		\resizebox{0.8\textwidth}{!}{
		 \begin{tabular}{||l c c c c||}
			\hline
			 & \multicolumn{4}{|c|}{$r^2$ by mouse} \\
			 \hline
			 Organoids (C3(1)tag mice) & 1 & 2 & 3 & 4  \\ [0.5ex]
			 \hline\hline
			  \textbf{Peripheral sum K14} & \textbf{0.11} & \textbf{0.25} & 0.06 & 0.03 \\
			 \hline
			 Centeral sum K14 & 0.01 & 0.03 & 0.06 & 0.00\\
			 \hline
			 Entire sum K14 & 0.01 & 0.00 & 0.01 & 0.00\\
			 \hline
%			 K14 Mean & 0.02 & 0.04 & 0.03 & xx\\ [1ex]
%			 \hline
			Organoid size & 0.07 & 0.01 & \textbf{0.07} &  \textbf{0.06} \\
			 \hline
		\end{tabular}
		}
\end{table}

Start adding figures here.\\
Q: Are we keeping the large vs. small organoids?
Q: should this be split into PyMT section and C31Tag section?

Fig. 1: show each step in the pipeline from DCI to spectral score for 2 organoids (one with low spectral score and one with high spectral score).

Fig. 2: show figures for the convolution kernel used to get peripheral K14 expression.

Fig. 3: Correlation plots PyMT

Fig. 4: Correlation plots C31Tag

Table 1: Summary statistics

\begin{comment}
% Place tables after the first paragraph in which they are cited.
\begin{table}[!ht]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{
{\bf Table caption Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.}}
\begin{tabular}{|l+l|l|l|l|l|l|l|}
\hline
\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \thickhline
$cell1 row1$ & cell2 row 1 & cell3 row 1 & cell4 row 1 & cell5 row 1 & cell6 row 1 & cell7 row 1 & cell8 row 1\\ \hline
$cell1 row2$ & cell2 row 2 & cell3 row 2 & cell4 row 2 & cell5 row 2 & cell6 row 2 & cell7 row 2 & cell8 row 2\\ \hline
$cell1 row3$ & cell2 row 3 & cell3 row 3 & cell4 row 3 & cell5 row 3 & cell6 row 3 & cell7 row 3 & cell8 row 3\\ \hline
\end{tabular}
\begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl. Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
\end{flushleft}
\label{table1}
\end{adjustwidth}
\end{table}
\end{comment}

%PLOS does not support heading levels beyond the 3rd (no 4th level headings).
\subsection*{\lorem\ and \ipsum\ nunc blandit a tortor}
\subsubsection*{3rd level heading}

\begin{enumerate}
	\item{react}
	\item{diffuse free particles}
	\item{increment time by dt and go to 1}
\end{enumerate}

\section*{Discussion}
%Nulla mi mi, venenatis sed ipsum varius, Table~\ref{table1} volutpat euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent faucibus semper libero~\cite{bib3}.

We implemented a method to quanitfy the invasive phenotypes organoids derived from two distinct mouse models, namely PyMT and C3(1)tag.\\
Out of the features we tested, we found that peripheral K14 expression correlated with the invasive phenotype.\\
Why is this important and/or interesting?\\
Future directions: Test our method on Patient derived organoids, PDOs.\\
Does organoid invasion score correlate with patient outcome?

\section*{Conclusion}

CO\textsubscript{2} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque. Quisque augue sem, tincidunt sit amet feugiat eget, ullamcorper sed velit.

Sed non aliquet felis. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Mauris commodo justo ac dui pretium imperdiet. Sed suscipit iaculis mi at feugiat. Ut neque ipsum, luctus id lacus ut, laoreet scelerisque urna. Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl. Ut ornare mauris tellus, vel dapibus arcu suscipit sed. Nam condimentum sem eget mollis euismod. Nullam dui urna, gravida venenatis dui et, tincidunt sodales ex. Nunc est dui, sodales sed mauris nec, auctor sagittis leo. Aliquam tincidunt, ex in facilisis elementum, libero lectus luctus est, non vulputate nisl augue at dolor. For more information, see \nameref{S1_Appendix}.

\section*{Supporting information}

% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
\paragraph*{S1 Fig.}
\label{S1_Fig}
{\bf Bold the title sentence.} Add descriptive text after the title of the item (optional).

\paragraph*{S2 Fig.}
\label{S2_Fig}
{\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\paragraph*{S1 File.}
\label{S1_File}
{\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\paragraph*{S1 Video.}
\label{S1_Video}
{\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\paragraph*{S1 Appendix.}
\label{S1_Appendix}
{\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\paragraph*{S1 Table.}
\label{S1_Table}
{\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\section*{Acknowledgments}
Cras egestas velit mauris, eu mollis turpis pellentesque sit amet. Interdum et malesuada fames ac ante ipsum primis in faucibus. Nam id pretium nisi. Sed ac quam id nisi malesuada congue. Sed interdum aliquet augue, at pellentesque quam rhoncus vitae.

\nolinenumbers

% Either type in your references using
% \begin{thebibliography}{}
% \bibitem{}
% Text
% \end{thebibliography}
%
% or
%
% Compile your BiBTeX database using our plos2015.bst
% style file and paste the contents of your .bbl file
% here. See http://journals.plos.org/plosone/s/latex for 
% step-by-step instructions.
% 
\begin{thebibliography}{10}

\bibitem{Schneider:2012ui}
Schneider CA, Rasband WS, Eliceiri KW.
\newblock {NIH Image to ImageJ: 25 years of image analysis.}
\newblock Nature methods. 2012;9(7):671--675.

\end{thebibliography}

\end{document}

### 2018-12-07 docs/01_paper/paper.tex
Added authors and edited abstract

@@
+% Template for PLoS
+% Version 3.5 March 2018
 %
-\documentclass[runningheads]{llncs}
+% % % % % % % % % % % % % % % % % % % % % %
 %
-\usepackage{graphicx}
+% -- IMPORTANT NOTE
+%
+% This template contains comments intended 
+% to minimize problems and delays during our production 
+% process. Please follow the template instructions
+% whenever possible.
+%
+% % % % % % % % % % % % % % % % % % % % % % % 
+%
+% Once your paper is accepted for publication, 
+% PLEASE REMOVE ALL TRACKED CHANGES in this file 
+% and leave only the final text of your manuscript. 
+% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
+% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
+%
+%
+% There are no restrictions on package use within the LaTeX files except that 
+% no packages listed in the template may be deleted.
+%
+% Please do not include colors or graphics in the text.
+%
+% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
+%
+% % % % % % % % % % % % % % % % % % % % % % %
+%
+% -- FIGURES AND TABLES
+%
+% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
+%
+% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
+% - Figures should be uploaded separately from your manuscript file. 
+% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
+% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
+% For figure citations, please use "Fig" instead of "Figure".
+% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
+%
+% Tables should be cell-based and may not contain:
+% - spacing/line breaks within cells to alter layout or alignment
+% - do not nest tabular environments (no tabular environments within tabular environments)
+% - no graphics or colored text (cell background color/shading OK)
+% See http://journals.plos.org/plosone/s/tables for table guidelines.
+%
+% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
+%
+% % % % % % % % % % % % % % % % % % % % % % % %
+%
+% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
+%
+% IMPORTANT
+% Below are a few tips to help format your equations and other special characters according to our specifications.
+For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
+%
+% For inline equations, please be sure to include all portions of an equation in the math environment.
+For example, x$^2$ is incorrect; this should be formatted as $x^2$ (or $\mathrm{x}^2$ if the romanized font is desired).
+%
+% Do not include text that is not math in the math environment. For example, CO2 should be written as CO\textsubscript{2} instead of CO$_2$.
+%
+% Please add line breaks to long display equations when possible in order to fit size of the column. 
+%
+% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
+%
+% When adding superscript or subscripts outside of brackets/braces, please group using {}.  For example, change "[U(D,E,\gamma)]^2" to "{[U(D,E,\gamma)]}^2". 
+%
+% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
+%
+% % % % % % % % % % % % % % % % % % % % % % % % 
+%
+% Please contact latex@plos.org with any questions.
+%
+% % % % % % % % % % % % % % % % % % % % % % % %
+
+\documentclass[10pt,letterpaper]{article}
+\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
+
+% amsmath and amssymb packages, useful for mathematical formulas and symbols
+\usepackage{amsmath,amssymb}
+
+% Use adjustwidth environment to exceed column width (see example table in text)
+\usepackage{changepage}
+
+% For commenting
 \usepackage{comment}
-\usepackage{xcolor}
-% Used for displaying a sample figure. If possible, figure files should
-% be included in EPS format.
-%
-% If you use the hyperref package, please uncomment the following line
-% to display URLs in blue roman font according to Springer's eBook style:
-% \renewcommand\UrlFont{\color{blue}\rmfamily}
+
+% Use Unicode characters when possible
+\usepackage[utf8x]{inputenc}
+
+% textcomp package and marvosym package for additional characters
+\usepackage{textcomp,marvosym}
+
+% cite package, to clean up citations in the main text. Do not remove.
+\usepackage{cite}
+
+% Use nameref to cite supporting information files (see Supporting Information section for more info)
+\usepackage{nameref,hyperref}
+
+% line numbers
+\usepackage[right]{lineno}
+
+% ligatures disabled
+\usepackage{microtype}
+\DisableLigatures[f]{encoding = *, family = * }
+
+% color can be used to apply background shading to table cells only
+\usepackage[table]{xcolor}
+
+% array package and thick rules for tables
+\usepackage{array}
+
+% create "+" rule type for thick vertical lines
+\newcolumntype{+}{!{\vrule width 2pt}}
+
+% create \thickcline for thick horizontal lines of variable length
+\newlength\savedwidth
+\newcommand\thickcline[1]{%
+  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
+  \cline{#1}%
+  \noalign{\vskip\arrayrulewidth}%
+  \noalign{\global\arrayrulewidth\savedwidth}%
+}
+
+% \thickhline command for thick horizontal lines that span the table
+\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
+\hline
+\noalign{\global\arrayrulewidth\savedwidth}}
+
+% Remove comment for double spacing
+%\usepackage{setspace} 
+%\doublespacing
+
+% Text layout
+\raggedright
+\setlength{\parindent}{0.5cm}
+\textwidth 5.25in 
+\textheight 8.75in
+
+% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
+% Captions will be left justified
+\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
+\renewcommand{\figurename}{Fig}
+
+% Use the PLoS provided BiBTeX style
+\bibliographystyle{plos2015}
+
+% Remove brackets from numbering in List of References
+\makeatletter
+\renewcommand{\@biblabel}[1]{\quad#1.}
+\makeatother
+
+% Header and Footer with logo
+\usepackage{lastpage,fancyhdr,graphicx}
+\usepackage{epstopdf}
+%\pagestyle{myheadings}
+\pagestyle{fancy}
+\fancyhf{}
+%\setlength{\headheight}{27.023pt}
+%\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
+\rfoot{\thepage/\pageref{LastPage}}
+\renewcommand{\headrulewidth}{0pt}
+\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
+\fancyheadoffset[L]{2.25in}
+\fancyfootoffset[L]{2.25in}
+\lfoot{\today}
+
+%% Include all macros below
+
+\newcommand{\lorem}{{\bf LOREM}}
+\newcommand{\ipsum}{{\bf IPSUM}}
+
+%% END MACROS SECTION
 
 \begin{document}
+\vspace*{0.2in}
+
+% Title must be 250 characters or less.
+\begin{flushleft}
+{\Large
+\textbf\newline{Membrane-localized Keratin-14 Promotes Invasion} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
+}
+\newline
+% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
+\\
+Yohannes Tsehay\textsuperscript{1},
+Hildur Knutsodottir\textsuperscript{1},
+Andrei Kucharavy\textsuperscript{1\textcurrency},
+Veena Padmanaban\textsuperscript{2},
+Joel Bader\textsuperscript{1*}
+%with the Lorem Ipsum Consortium\textsuperscript{\textpilcrow}
+\\
+\bigskip
+\textbf{1} High-Throughout Biology Center and Department of Biomedical Engineering, Johns Hopkins University, Baltimore, MD, USA
+\\
+\textbf{2} Center for Cell Dynamics and Department of Cell Biology, Johns Hopkins University School of Medicine, Baltimore, MD, USA
+\\
+\bigskip
+
+% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
 % 
-\title{Membrane-localized Keratin-14 Promotes Invasion\thanks{Supported by organization x.}}
+% Remove or comment out the author notes below if they aren't used.
 %
-%\titlerunning{Abbreviated paper title}
-% If the paper title is too long for the running head, you can set
-% an abbreviated paper title here
-%
-\author{First Author \inst{1}\orcidID{0000-1111-2222-3333} \and
-Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
-Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
-%
-\authorrunning{F. Author et al.}
-% First names are abbreviated in the running head.
-% If there are more than two authors, 'et al.' is used.
-%
-\institute{Johns Hopkins University
-\url{http://www} \and
-Other\\
-\email{\{bla,blu\}@jhu.edu}}
-%
-\maketitle              % typeset the header of the contribution
-%
-\begin{abstract}
-Metastasis is the main predictor of outcome for patients with cancer, yet the molecular mechanism driving invasive phenotypes is not well understood.
+% Primary Equal Contribution Note
+%\Yinyang These authors contributed equally to this work.
+
+% Additional Equal Contribution Note
+% Also use this double-dagger symbol for special authorship notes, such as senior authorship.
+%\ddag These authors also contributed equally to this work.
+
+% Current address notes
+\textcurrency Current Address: Dept/Program/Center, Institution Name, City, State, Country % change symbol to "\textcurrency a" if more than one current address note
+% \textcurrency b Insert second current address 
+% \textcurrency c Insert third current address
+
+% Deceased author note
+%\dag Deceased
+
+% Group/Consortium Author Note
+%\textpilcrow Membership list can be found in the Acknowledgments section.
+
+% Use the asterisk to denote corresponding authorship and provide email address in note below.
+* joel.bader@jhu.edu
+
+\end{flushleft}
+% Please keep the abstract below 300 words
+\section*{Abstract}
+Metastasis is the main predictor of outcome for patients with cancer, yet the molecular mechanism driving invasive phenotypes is not well under-stood, hindering development of assays and therapeutics for this stage of cancer progression.
+In this study, we characterize a molecular biomarker for invasion in greater detail, using an automated computer model.
+The model quantifies the invasive potential of tumors, allowing for quantification of even minor contributions to an invasive phenotype from individual genes, and can potentially be used to establish interactions among genes.
 Keratin 14 (K14) is a known molecular biomarker that is correlated with poor outcomes in breast cancer patients.
-In this study, we apply our automated computer model that quantifies the invasive potential of tumors to characterize K14 expression as it relates to invasion.
-We test the hypothesis that K14 is directly correlated to invasion versus the alternative hypothesis that size is the main predictor.
-We used two different transgenic mice (PyMT and C3(1)-Tag) as our breast cancer tumor models.
-Organoids were generated from these mice, and each organoid had a corresponding differential interference contrast image, K14 image, and an invasive potential score generated using our automated system.
+We apply our automated computer model, which was built in Python, to test the hypothesis that K14 is directly correlated with automatically generated invasion scores, independent of tumor size.
+We used two different transgenic mice as our breast cancer tumor models.
+Organoids were generated from these mice, and each organoid had a corresponding differential interference contrast image, K14 image, and a boundary around the organoid drawn manually which was used to generate an invasion score for the organoid using our automated system.
 The parameters assessed include the following: entire K14 expression, peripheral K14 expression (edges of the organoid), central K14 expression (center of the organoid), and organoid size.
-Peripheral K14 expression showed the strongest correlation with invasion scores for both types of transgenic mice.
-The results suggest that K14 expression in cells located in the periphery may be an important marker of invasion.
+Peripheral K14 expression showed the strongest correlation with invasion scores for both types of transgenic mice, suggesting that K14 expression in cells located in the periphery may be an important marker of invasion.
+This relationship was more prominent in one mouse model than the other, indicating that additional factors play a role in invasion and dissemination.
+In future studies, we plan to perform a similar analysis using human organoids generated from breast tumors.
 
-\keywords{Metastasis \and Tumor Invasion \and Keratin 14 \and Spectral Analysis \and ...}
-\end{abstract}
-%
-%
-%
-\section{Introduction}
+% Please keep the Author Summary between 150 and 200 words
+% Use first person. PLOS ONE authors please skip this step. 
+% Author Summary not valid for PLOS ONE submissions.   
+\section*{Author summary}
+
+\linenumbers
+
+% Use "Eq" instead of "Equation" for equation citations.
+\section*{Introduction}
+%Lorem ipsum dolor sit~\cite{bib1} amet, consectetur adipiscing elit.
+Curabitur eget porta erat.
+Morbi consectetur est vel gravida pretium.
+Suspendisse ut dui eu ante cursus gravida non sed sem.
+Nullam Eq~(\ref{eq:schemeP}) sapien tellus, commodo id velit id, eleifend volutpat quam.
+Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus.
+Nunc pellentesque pretium diam, quis maximus dolor faucibus id.~\cite{bib2} Nunc convallis sodales ante, ut ullamcorper est egestas vitae.
+Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.
 
@@
 
-\section {Methods}
+%\begin{eqnarray}
+%\label{eq:schemeP}
+%	\mathrm{P_Y} = \underbrace{H(Y_n) - H(Y_n|\mathbf{V}^{Y}_{n})}_{S_Y} + \underbrace{H(Y_n|\mathbf{V}^{Y}_{n})- %H(Y_n|\mathbf{V}^{X,Y}_{n})}_{T_{X\rightarrow Y}},
+%\end{eqnarray}
 
-Fig. 0: Make figure showing the 'pipeline'.
-
-\textcolor{blue}{
-\begin{itemize}
-    \item Experimental protocol. Ask Veena to write this part.\\ 
-        100-300 organoids from 4 mice.
-    \item Image acquisition and organoid periphery. Veena.\\
-        Use ImageJ to mark the periphery of the organoids from DIC microscope images.
-    \item Image segmentation. Andrei to write about convolution kernel.
-    \item Spectral score. Reference Joel's paper. Disclose scripts?
-\end{itemize}
-}
-
-\subsection{Data acquisition}
+\section*{Materials and methods}
+\subsection*{Data acquisition}
 
@@
 
-\subsection{Spectral Analysis}
-A method described in REF.\\
-Able to distinguish quantitative phenotypes.
+% For figure citations, please use "Fig" instead of "Figure".
+% Nulla mi mi, Fig~\ref{fig1} venenatis sed ipsum varius, volutpat euismod diam.
+Proin rutrum vel massa non gravida.
+Quisque tempor sem et dignissim rutrum.
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Morbi at justo vitae nulla elementum commodo eu id massa.
+In vitae diam ac augue semper tincidunt eu ut eros.
+Fusce fringilla erat porttitor lectus cursus, \nameref{S1_Video} vel sagittis arcu lobortis.
+Aliquam in enim semper, aliquam massa id, cursus neque.
+Praesent faucibus semper libero.
 
-\subsection{Convolution kernel}
-ANDREI
+% Results and Discussion can be combined.
+\section*{Results}
+% Nulla mi mi, venenatis sed ipsum varius, Table~\ref{table1} volutpat
 
-\subsection{Correlation Analysis}
-
-\begin{figure}
+\begin{figure}[!h]
 \includegraphics[width=\textwidth]{Image1.pdf}
@@
 \textcolor{red}{Axis font needs to be bigger.
-Y-axis in spectral score should all be the same and we can probably skip column 2.}} \label{fig1}
+Y-axis in spectral score should all be the same and we can probably skip column 2.}}
+\label{fig1}
 \end{figure}
 
-\section{Results}
+\begin{figure}[!h]
+\centering
+\includegraphics[width=\textwidth]{docs/01_paper/mouse_1_Day5_FA.pdf}
+\caption{comment} 
+\label{fig2}
+\end{figure}
+
+\begin{figure}[!h]
+\includegraphics[width=\textwidth]{docs/01_paper/mouse_1_Day5_KPS.pdf}
+\caption{comment} 
+\label{fig3}
+\end{figure}
+
+\begin{figure}[!h]
+\includegraphics[width=\textwidth]{docs/01_paper/mouse_1_Day5_KCS.pdf}
+\caption{comment} 
+\label{fig4}
+\end{figure}
+
+\begin{figure}[!h]
+\includegraphics[width=\textwidth]{docs/01_paper/mouse_1_Day5_KS.pdf}
+\caption{comment} 
+\label{fig4}
+\end{figure}
 
 \begin{table}
-\caption{Peripheral K14 explains correlates with invasive potential the best.}\label{tab1}
+\caption{{\bf Peripheral K14 explains correlates with invasive potential the best.}}
+\label{tab1}
 		\centering
@@
 \begin{table}
-\caption{Peripheral K14 explains correlates with invasive potential the best.}\label{tab1}
+\caption{{\bf Peripheral K14 explains correlates with invasive potential the best.}}
+\label{tab1}
 		\centering
@@
 
-\section{Discussion}
+\begin{comment}
+% Place tables after the first paragraph in which they are cited.
+\begin{table}[!ht]
+\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\centering
+\caption{
+{\bf Table caption Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.}}
+\begin{tabular}{|l+l|l|l|l|l|l|l|}
+\hline
+\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \thickhline
+$cell1 row1$ & cell2 row 1 & cell3 row 1 & cell4 row 1 & cell5 row 1 & cell6 row 1 & cell7 row 1 & cell8 row 1\\ \hline
+$cell1 row2$ & cell2 row 2 & cell3 row 2 & cell4 row 2 & cell5 row 2 & cell6 row 2 & cell7 row 2 & cell8 row 2\\ \hline
+$cell1 row3$ & cell2 row 3 & cell3 row 3 & cell4 row 3 & cell5 row 3 & cell6 row 3 & cell7 row 3 & cell8 row 3\\ \hline
+\end{tabular}
+\begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl.
+Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
+\end{flushleft}
+\label{table1}
+\end{adjustwidth}
+\end{table}
+\end{comment}
+
+%PLOS does not support heading levels beyond the 3rd (no 4th level headings).
+\subsection*{\lorem\ and \ipsum\ nunc blandit a tortor}
+\subsubsection*{3rd level heading}
+
+\begin{enumerate}
+	\item{react}
+	\item{diffuse free particles}
+	\item{increment time by dt and go to 1}
+\end{enumerate}
+
+\section*{Discussion}
+%Nulla mi mi, venenatis sed ipsum varius, Table~\ref{table1} volutpat euismod diam.
+Proin rutrum vel massa non gravida.
+Quisque tempor sem et dignissim rutrum.
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Morbi at justo vitae nulla elementum commodo eu id massa.
+In vitae diam ac augue semper tincidunt eu ut eros.
+Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis.
+Aliquam in enim semper, aliquam massa id, cursus neque.
+Praesent faucibus semper libero~\cite{bib3}.
+
 We implemented a method to quanitfy the invasive phenotypes organoids derived from two distinct mouse models, namely PyMT and C3(1)tag.\\
@@
 
-\section{Conclusion}
+\section*{Conclusion}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{comment}
-\begin{table}
-\caption{Table captions should be placed above the
-tables.}\label{tab1}
-\begin{tabular}{|l|l|l|}
-\hline
-Heading level &  Example & Font size and style\\
-\hline
-Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
-1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
-2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
-3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
-4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
-\hline
-\end{tabular}
-\end{table}
+\section*{Supporting information}
 
-\noindent Displayed equations are centered and set on a separate
-line.
-\begin{equation}
-x + y = z
-\end{equation}
-Please try to avoid rasterized images for line-art diagrams and
-schemas. Whenever possible, use vector graphics instead (see
-Fig.~\ref{fig1}).
+% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
+\paragraph*{S1 Fig.}
+\label{S1_Fig}
+{\bf Bold the title sentence.} Add descriptive text after the title of the item (optional).
 
-\begin{figure}
-\includegraphics[width=\textwidth]{fig1.eps}
-\caption{A figure caption is always placed below the illustration.
-Please note that short captions are centered, while long ones are
-justified by the macro package automatically.} \label{fig1}
-\end{figure}
+\paragraph*{S2 Fig.}
+\label{S2_Fig}
+{\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
+Etiam eget sapien nibh.
+Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
+Curabitur fringilla pulvinar lectus consectetur pellentesque.
 
-\begin{theorem}
-This is a sample theorem. The run-in heading is set in bold, while
-the following text appears in italics. Definitions, lemmas,
-propositions, and corollaries are styled the same way.
-\end{theorem}
+\paragraph*{S1 File.}
+\label{S1_File}
+{\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida.
+Etiam eget sapien nibh.
+Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
+Curabitur fringilla pulvinar lectus consectetur pellentesque.
+
+\paragraph*{S1 Video.}
+\label{S1_Video}
+{\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida.
+Etiam eget sapien nibh.
+Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
+Curabitur fringilla pulvinar lectus consectetur pellentesque.
+
+\paragraph*{S1 Appendix.}
+\label{S1_Appendix}
+{\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
+Etiam eget sapien nibh.
+Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
+Curabitur fringilla pulvinar lectus consectetur pellentesque.
+
+\paragraph*{S1 Table.}
+\label{S1_Table}
+{\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
+Etiam eget sapien nibh.
+Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
+Curabitur fringilla pulvinar lectus consectetur pellentesque.
+
+\section*{Acknowledgments}
+Cras egestas velit mauris, eu mollis turpis pellentesque sit amet.
+Interdum et malesuada fames ac ante ipsum primis in faucibus.
+Nam id pretium nisi.
+Sed ac quam id nisi malesuada congue.
+Sed interdum aliquet augue, at pellentesque quam rhoncus vitae.
+
+\nolinenumbers
+
+% Either type in your references using
+% \begin{thebibliography}{}
+% \bibitem{}
+% Text
+% \end{thebibliography}
 %
-% the environments 'definition', 'lemma', 'proposition', 'corollary',
-% 'remark', and 'example' are defined in the LLNCS documentclass as well.
+% or
 %
-\begin{proof}
-Proofs, examples, and remarks have the initial word in italics,
-while the following text appears in normal font.
-\end{proof}
-For citations of references, we prefer the use of square brackets
-and consecutive numbers. Citations using labels or the author/year
-convention are also acceptable. The following bibliography provides
-a sample reference list with entries for journal
-articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
-book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
-and a homepage~\cite{ref_url1}. Multiple citations are grouped
-\cite{ref_article1,ref_lncs1,ref_book1},
-\cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
+% Compile your BiBTeX database using our plos2015.bst
+% style file and paste the contents of your .bbl file
+% here. See http://journals.plos.org/plosone/s/latex for 
+% step-by-step instructions.
 % 
-% ---- Bibliography ----
-%
-% BibTeX users should specify bibliography style 'splncs04'.
-% References will then be sorted and formatted in the correct style.
-%
-% \bibliographystyle{splncs04}
-% \bibliography{mybibliography}
-%
-
-\end{comment}
-
-\begin{thebibliography}{8}
+\begin{thebibliography}{10}
 

### 2019-01-12 docs/01_paper/back-up.tex
Added more figures. Finished methods.

--- 2018-12-07 docs/01_paper/paper.tex
@@
 {\Large
-\textbf\newline{Membrane-localized Keratin-14 Promotes Invasion} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
+\textbf\newline{Morphological Features of Organoid Invasion are Correlated with Membrane-Localized Keratin-14 Expression} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
 }
@@
 \section*{Abstract}
-Metastasis is the main predictor of outcome for patients with cancer, yet the molecular mechanism driving invasive phenotypes is not well under-stood, hindering development of assays and therapeutics for this stage of cancer progression.
+Metastasis is the main predictor of outcome for patients with cancer, yet the molecular mechanism driving invasive phenotypes is not well understood, hindering development of assays and therapeutics for this stage of cancer progression.
 In this study, we characterize a molecular biomarker for invasion in greater detail, using an automated computer model.
@@
 \section*{Introduction}
+
+Metastasis is the main predictor of outcome for patients with cancer.
+The relative 5 year survival rate in patients with breast cancer in situ, regional spread, and distant metastasis are $99\%$, $85\%$, and $26\%$ respectively\cite{Siegel:2017cs}.
+The survival rates for all stages of breast cancer have improved substantially, but much of the improvement is seen among patients with regional stage cancer with a 5-year relative survival rate increase from $68\%$ to $89\%$ in white women and $55\%$ to $81\%$ in black women.
+The improvements seen are largely due to adjuvent antineoplasitc, hormonal, and targeted therapy, and early tumor detection with mammograms \cite{DeSantis:2017BC}.
+Secular trends of tumor size within each stage of the disease (local, regional, and distant) has been decreasing since 1975 due to early detection of tumors\cite{Elkin:2005cts}, yet tumor size or even other tumor characteristics such as estrogen receptor status do not explain this positive trend in survival rates especially in patients younger than 70 years of age \cite{Park:2015ibc}.
+Thus, it is important to further our understanding of the molecular mechanism of tumor invasion and dissemination to support the development of therapeutics that can improve outcomes for patients with invasive carcinoma and establish biomarkers that accurately predict patient prognosis.
+
+Three-dimentional organotypic culture techniques can be used to model disease processes in vitro.
+Tissue samples can be harvested from human or murine donors and processed by mechanical disruption, enzymatic digestion, and centrifugation into tissue fragments known as organoids which are explanted into a commercial extracellular matrix such as Matrigel or collagen I\cite {Shamir:2014td}.
+This experimental technique combined with transgenic mice tissue donors allows for a series of experiments that can elucidate the relationship between gene expression and phenotypic behavior of mammalian tissue.
+For example, MMTV-PyMT and C3(1)-TAg are two different transgenic mice that develop metastatic carcinoma of the breast\cite{Maroulakou:1994pm,Guy:1992im}.
+These mice have provided a supply of organoids used to study the invasive process of breast tumors\cite{Shamir:2014td,Cheung:2013ci,Cheung:2016pcb}.
+
+The various clinical and organotypic cell culturing studies have identified Keratin 14 (K14) as an important biomarker.
+K14 is a structural protein normally expressed in basal epithelial cells or myoepithelial cells.
+Its expression in luminal glandular cells, which seldom express K14, has been linked to decreased relapse-free survival and overall poor outcomes for patients with breast cancer\cite{Gusterson:2005bc,Laakso:2006blc}.
+Organotypic cell culture experiments have demonstrated that breast tumors are heterogeneous, and it is specifically the K14 expressing cells that initiate the invasion process.
+Furthermore, locally disseminated cells, circulating tumor cells and those that have seeded distant organs all frequently express K14\cite{Cheung:2013ci,Cheung:2016pcb}.
+However, how K14 promotes invasion, whether it be through cell signaling pathways, alterations in the cytoskeleton, or changes in a cell's relationship with other neighboring cells, remains unclear.
+
+Spectral Power
+
+Objective and hypothesis
+
 %Lorem ipsum dolor sit~\cite{bib1} amet, consectetur adipiscing elit.
@@
 
-Alternative title: Morphological features of organoid invasion are correlated with membrane-localized Keratin-14 expression
+%Alternative title: Morphological features of organoid invasion are correlated with membrane-localized Keratin-14 expression
 
@@
 
- A total of 4 PyMT and 4 C31T mice were used to generate a total of \{\} organoids, which were then cultured in collagen I gels for 5 days.
-At day 5, they were imaged, an average of 16 per sample.
+ A total of 4 PyMT and 4 C31T mice were used to generate a total of $1577$ ($880$ PyMT and $697$ C31T) organoids, which were then cultured in collagen I gels for 5 days.
+At day 5, they were imaged.
 Differential interference contrast (DIC) microscopy yielded 1040$\times$1388 pixel images.
@@
 
+\bibitem{Siegel:2017cs}
+Siegel, Rebecca L., Kimberly D. Miller, and Ahmedin Jemal. 
+\newblock {"Cancer statistics, 2017."}
+\newblock {CA: a cancer journal for clinicians 67.1 (2017): 7-30.}
+
+\bibitem{DeSantis:2017BC}
+DeSantis, Carol E., et al.
+\newblock {"Breast cancer statistics, 2017, racial disparity in mortality by state."}
+\newblock{CA: a cancer journal for clinicians 67.6 (2017): 439-448.}
+
+\bibitem{Elkin:2005cts}
+Elkin, Elena B., et al. 
+\newblock {"The effect of changes in tumor size on breast carcinoma survival in the US: 1975–1999."}
+\newblock {Cancer: Interdisciplinary International Journal of the American Cancer Society 104.6 (2005): 1149-1157.}
+
+\bibitem{Park:2015ibc}
+Park, Ju-Hyun, William F. Anderson, and Mitchell H. Gail. 
+\newblock {"Improvements in US breast cancer survival and proportion explained by tumor size and estrogen-receptor status."}
+\newblock {Journal of Clinical Oncology 33.26 (2015): 2870.}
+
+\bibitem {Shamir:2014td}
+Shamir, Eliah R., and Andrew J. Ewald.
+\newblock {"Three-dimensional organotypic culture: experimental models of mammalian biology and disease."}
+\newblock {Nature reviews Molecular cell biology 15.10 (2014): 647.}
+
+\bibitem {Maroulakou:1994pm}
+Maroulakou, Ioanna G., et al. 
+\newblock{"Prostate and mammary adenocarcinoma in transgenic mice carrying a rat C3 (1) simian virus 40 large tumor antigen fusion gene."} \newblock {Proceedings of the National Academy of Sciences 91.23 (1994): 11236-11240.}
+
+\bibitem {Guy:1992im}
+Guy, Chantale T., R. D. Cardiff, and William J. Muller. 
+\newblock {"Induction of mammary tumors by expression of polyomavirus middle T oncogene: a transgenic mouse model for metastatic disease."} \newblock {Molecular and cellular biology 12.3 (1992): 954-961.}
+
+\bibitem {Cheung:2013ci}
+Cheung, Kevin J., et al. 
+\newblock {"Collective invasion in breast cancer requires a conserved basal epithelial program."}
+\newblock {Cell 155.7 (2013): 1639-1651.}
+
+\bibitem {Cheung:2016pcb}
+Cheung, Kevin J., et al.
+\newblock{"Polyclonal breast cancer metastases arise from collective dissemination of keratin 14-expressing tumor cell clusters."}
+\newblock {Proceedings of the National Academy of Sciences 113.7 (2016): E854-E863.}
+
+\bibitem{Gusterson:2005bc}
+Gusterson, Barry A., et al. 
+\newblock {"Basal cytokeratins and their relationship to the cellular origin and functional classification of breast cancer."}
+\newblock {Breast Cancer Research 7.4 (2005): 143.}
+
+\bibitem{Laakso:2006blc}
+Laakso, Mervi, et al. 
+\newblock {"Basoluminal carcinoma: a new biologically and prognostically distinct entity between basal and luminal breast cancer."} \newblock {Clinical Cancer Research 12.14 (2006): 4185-4191.}
+
 \bibitem{Schneider:2012ui}
